---
title: "R Notebook"
output: html_notebook
---

Tidying the dye screening dataset

Final output: 
Assign unique indices for each curve
Format:

DSF01_S01_ID00001
- start with the DSFbase version
- then have a source identifier
- then have an individual curve identifier
- give each # a leading character so it does not reduce down to fewer leading zeroes when split
- add enough leading zeroes to accomodate 10 - 99,000 curves 

```{r}
library(tidyverse)
```
Automated test for database files
```{r}

```


Function to generate curve IDs
```{r}
make_IDS <- 
  function(input_vars, 
           dsfbase_version = 1,
           source_id = 1,
           ID_start = 1){

    
  out <- tibble(orig = input_vars,
      header = glue::glue("DSF00{dsfbase_version}_S0{source_id}")) |>
      mutate(
             id = paste0(header, "_", "ID",
                                         stringr::str_pad(row_number() + ID_start - 1, # the curve number
                                                          6, # to six places
                                                          pad = "0")) # left-pad zeroes
      )

    
  out$id
  }

make_IDS(c("two", "zed"))

```

Read in raw data
```{r}
# from dye screens
dye <- vroom::vroom("../00_raw_inputs/data_S3_dye_screen_results_raw.txt")

# from SYPRO
sypro <- read
```

```{r}
trim <-
  raw |> 
  select(variable, Temperature, value) |> 
  pivot_wider(id_cols = Temperature, 
              names_from = variable, 
              values_from = value)
```

Generate the ID map
This will almost certainly get re-generated in the end, 
oncewe decide how we want to order the data to make it more user-friendly
e.g. the first 500 are all SYPRO, the next 5,000 are with-protein hits, sensitives, the last bunch are EBPs...
```{r}
ID_map <- 
  tibble(original = names(trim)) |> 
  filter(original != "Temperature") |> 
  mutate(ID = make_IDS(original, source_id = 2)) |> 
  relocate(ID)

ID_map
```

Add IDs as names for each tibble
```{r}
final <- trim |> 
  set_names(c("Temperature", ID_map$ID))
```

Save the output file
```{r}
# 175 MB
final |> vroom::vroom_write("../01_intermediate_outputs/dye_screens_indexed.txt")
ID_map |> write_rds("../01_intermediate_outputs/dye_screens_index_map.rds")
```








