---
title: "R Notebook"
output: html_notebook
---

Tidying the dye screening dataset.

Step 1: Read in the pre-existing "hits by channel". 
 - Plot these hits
 - Manually amend assignments (likely move some or many to non-canon)
 - Re-plot and save the final output

Step 2: Determine channels for sensitives as well as hits. 
Do not do this manually -- it will be too slow. 
Use the auto-detector written in Exp1224. 
 - Plot these sensitives
 - Manually amend assignments (move some to canon? move many to nothing...)
 - Re-plot and save the final output

```{r}
library(tidyverse)
library(fs)
library(testthat)
source("R/collect_dsf_data.R") 
source("R/dye_screens_to_dsfbase.R") # reading, tidy, process, plot, and add dye screens from Exp1252 to dsfbase
```

#### See below for steps determining that Exp1252 was the correct data source for this experiment

Exp1252 - The most complete and tidiest version of this data. 
Includes automated channel selections for both hits and sensitive.
```{r}
BY_CHANNEL_1252 <- sort(fs::dir_ls("/Users/taiaseanwu/Box Sync/data/Exp1252--20211206_all_screens_aggregated_cleaned/__input_data/by_var_fit/final_aggregation/collected"))

str(screen)
# List of 2
#  $ ranked_channels: tibble [192 × 5] (S3: tbl_df/tbl/data.frame)
#   ..$ dye          : chr [1:192] "A003" "A003" "A003" "A003" ...
#   ..$ dye_channel_f: chr [1:192] "A003_FAM" "A003_JOE" "A003_TAMRA" "A003_ROX" ...
#   ..$ norm_auc     : num [1:192] 46.37 1.2 3.24 3.38 3.27 ...
#   ..$ auc_rank     : int [1:192] 6 1 3 5 4 2 5 4 6 3 ...
#   ..$ auc_hit      : chr [1:192] "fit" "drop" "drop" "drop" ...
#  $ hit_channels_df: gropd_df [13,440 × 10] (S3: grouped_df/tbl_df/tbl/data.frame)
#   ..$ variable        : chr [1:13440] "A1_FAM_protein" "A19_FAM_protein" "A20_FAM_protein" "A24_FAM_protein" ...
#   ..$ Temperature     : num [1:13440] 25 25 25 25 25 25 25 25 25 25 ...
#   ..$ value           : num [1:13440] 1036 7273 16513 28505 608 ...
#   ..$ dye_conc_uM     : num [1:13440] 10 50 50 50 50 50 50 50 50 50 ...
#   ..$ dye_channel_f   : chr [1:13440] "SYPRO_FAM" "C018_FAM" "C019_FAM" "T004_FAM" ...
#   ..$ type            : chr [1:13440] "protein" "protein" "protein" "protein" ...
#   ..$ value_norm      : num [1:13440] 0.386 0.99 1 1 0.55 ...
#   ..$ exp_num         : chr [1:13440] "Ds0005" "Ds0005" "Ds0005" "Ds0005" ...
#   ..$ identity        : chr [1:13440] "lysozyme" "lysozyme" "lysozyme" "lysozyme" ...
#   ..$ value_group_norm: num [1:13440] 0.578 0.99 1 1 0.574 ...
```

Brief function reference for "R/dye_screens_to_dsfbase.R"
```{r}
## ---- Main function -- read, test, plot, save, and edit subsets from a dye screen
# test_plot_save_1252(PATH, 
#                     save_path = "../02_aggregated_data/dye_screen_tests/", 
#                     save_data = TRUE, 
#                     min_value = 10000, # filter out low-signal, noisy data. we have more than we need anyway
#                     min_range = 10000, # filter out low-signal, noisy data. we have more than we need anyway
#
#                     # after running once, inspect plots and re-run with manual edits to labels
#                     add_to_canon = c(), 
#                     drop_from_canon = c(), 
#                                 
#                     add_to_noncanon = c(), 
#                     drop_from_noncanon = c(), 
#                                 
#                     add_to_SYPRO_canon = c(),
#                     drop_from_SYPRO_canon = c(),
#                                 
#                     add_to_SYPRO_noncanon = c(),
#                     drop_from_SYPRO_noncanon = c(),
#                                 
#                     add_to_gotcha = c(),
#                     ...) 


## ---- helper functions for test_plot_save_1252
## ---- read a screen from Exp1252, and tidy it for inclusion in DSFbase
# screen <- tidy_1252(PATH, subset = "canon", ...)

## ---- helper function for `test_plot_save_1252()` to manually edit subsets from a dataframe 
# save_subset <-
#   function(dsf,
#            keep_assignment = "hit", 
#            keep_variable = c(),
#            drop_variable = c(),
#            .subset,
#            save_data = TRUE,
#            save_path = "../02_aggregated_data/dye_screen_tests/",
#            ...)

## ---- move all screens from interim dye_screens directory to main dsfbase directory
## ---- print dsfbase tally afterwards
# move_and_tally() 
```

Go by dye screens one-by-one
See workflowy for history of all manual edits for all screens
Workflowy internal link: https://workflowy.com/#/52c4edf81942
```{r}
# i <- 0 # only run once
i <- i + 1
print(i)
test_plot_save_1252(BY_CHANNEL_1252[i], 
                    min_range = 10000,
                    save_data = TRUE,
                    drop_from_canon = c("A24_FAM_protein", "B3_FAM_protein", "G22_ROX_protein"),
                    move_to_noncanon = c("A24_FAM_protein", "B3_FAM_protein", "G22_ROX_protein"),
                    drop_from_noncanon = c("E13_ROX_protein","E15_Cy5.5_protein","H12_FAM_protein","H5_TAMRA_protein", "K19_TAMRA_protein","L3_ROX_protein", "K24_ROX_protein"),
                    add_to_gotcha = c("H12_FAM_protein","H5_TAMRA_protein","K19_TAMRA_protein","L3_ROX_protein")) 

"A10_TAMRA_protein", "D14_TAMRA_protein", "D22_TAMRA_protein", "E12_ROX_protein", "E13_ROX_protein", "E14_Cy5.5_protein", "E15_Cy5.5_protein", "E19_FAM_protein", "E23_ROX_protein", "G1_FAM_protein", "G11_FAM_protein", "G13_JOE_protein", "G7_FAM_protein", "H12_FAM_protein", "H14_Cy5.5_protein", "H21_ROX_protein", "H5_TAMRA_protein", "K17_TAMRA_protein", "K19_TAMRA_protein", "K20_ROX_protein", "K21_TAMRA_protein", "K22_Cy5_protein", "K24_ROX_protein", "L1_Cy5_protein", "L3_ROX_protein"
```
Every once in a while, move the completed dye screens and calculate new tallies
```{r}
move_and_tally()
```





```{r}
test_plot_save_1252 <- function(PATH, 
                            subset = "canon",
                           save_path = "../02_aggregated_data/dye_screen_tests/", 
                           min_value = 10000,
                           min_range = 10000,
                           add_to_canon = c(),
                           drop_from_canon = c(),
                    
                           add_to_noncanon = c(),
                           drop_from_noncanon = c(),
                    
                           add_to_SYPRO_canon = c(),
                           drop_from_SYPRO_canon = c(),
                    
                           add_to_SYPRO_noncanon = c(),
                           drop_from_SYPRO_noncanon = c(),
                           ...) {
  
  # read in and tidy the Exp1252 dataset
  dsf <- tidy_1252(PATH, subset = subset, ...) |> 
    group_by(dye) |> 
    
    # drop low-signal curves, for simplicity
    filter(any(value > min_value), 
           any(max(value) - min(value) > min_range)) |> 
    ungroup()
  
  # make name for saving
  exp_num <- unique(dsf$exp_num)
  protein_name <- unique(dsf$protein)
  
  dataset_name <- glue::glue("{exp_num}_{protein_name}") 
  
  test_dataset(dsf)
  print_tallies(dsf)
  
  ####### ----- If SYPRO data, save hits to "SYPRO_canon" ----- 
  if("SYPRO" %in% dsf$dye) {
    sypro <-  dsf |> 
     filter(dye == "SYPRO")
    
    if("hit" %in% sypro$assignment) {
     sypro_canon <-  sypro |> 
     filter(assignment == "hit" | variable %in% add_to_SYPRO_canon,
            !variable %in% drop_from_SYPRO_canon) |> 
     mutate(subset = "SYPRO_canon")
   
    SYPRO_canon_name <- glue::glue("{dataset_name}_SYPRO_canon")
    
    # print("Saving SYPRO canon")
    test_plot_save(sypro_canon,
                     use_external_name = TRUE,
                     external_name = SYPRO_canon_name,
                    save_path = save_path) 
    
    } 
    
    if ("sensitive" %in% sypro$assignment) {
      sypro_noncanon <-  sypro |> 
         filter(assignment == "sensitive" | variable %in% add_to_SYPRO_noncanon,
                !variable %in% drop_from_SYPRO_noncanon) |> 
         mutate(subset = "SYPRO_noncanon")
      
      SYPRO_noncanon_name <- glue::glue("{dataset_name}_SYPRO_noncanon")
   
    # print("Saving SYPRO noncanon")
    # test_dataset(sypro_noncanon)
    # print_tallies(sypro_noncanon)
      
    test_plot_save(sypro_noncanon,
                     use_external_name = TRUE,
                     external_name = SYPRO_noncanon_name,
                   save_path = save_path) 
    }
  }
    
    
  ####### ----- Save non-SYPRO data to canon and noncanon ----- 
  if(!all(dsf$dye == "SYPRO"))  { # if there are non-SYPRO dyes 
    aurora <-  dsf |> 
     filter(dye != "SYPRO")
    
    if("hit" %in% aurora$assignment) {
     aurora_canon <-  aurora |> 
     filter(assignment == "hit" | variable %in% add_to_canon,
            !variable %in% drop_from_canon) |> 
     mutate(subset = "canon")
   
    aurora_canon_name <- glue::glue("{dataset_name}_canon")
   
    print("Saving aurora canon")
    # test_dataset(aurora_canon)
    # print_tallies(aurora_canon)
      
    test_plot_save(aurora_canon,
                     use_external_name = TRUE,
                     external_name = aurora_canon_name,
                    save_path = save_path) 
    
    } 
    
    if ("sensitive" %in% aurora$assignment) {
      aurora_noncanon <-  aurora |> 
         filter(assignment == "sensitive" | variable %in% add_to_noncanon,
                !variable %in% drop_from_noncanon) |> 
         mutate(subset = "noncanon")
      
      aurora_noncanon_name <- glue::glue("{dataset_name}_noncanon")
   
    print("Saving aurora noncanon")
    test_dataset(aurora_noncanon)
    print_tallies(aurora_noncanon)
      
    test_plot_save(aurora_noncanon,
                     use_external_name = TRUE,
                     external_name = aurora_noncanon_name,
                     save_path = save_path) 
    }
  
  }
  
}

test_plot_save_1252(BY_CHANNEL_1252[1], 
                    save_path = "../02_aggregated_data/dye_screen_tests",
                           add_to_canon = c("D23_TAMRA_protein"),
                           drop_from_canon = c("L18_FAM_protein"),
                    
                           add_to_noncanon = c("L18_FAM_protein"),
                           drop_from_noncanon = c("G2_FAM_protein", "H15_Cy5.5_protein", "L16_FAM_protein", "D23_TAMRA_protein"),
                    
                           add_to_SYPRO_canon = c(),
                           drop_from_SYPRO_canon = c(),
                    
                           add_to_SYPRO_noncanon = c(),
                           drop_from_SYPRO_noncanon = c()
                           )
```
```{r}
screen <- tidy_1252(BY_CHANNEL_1252[1])
```

Do the first 10 screens
```{r}
lapply(BY_CHANNEL_1252, test_plot_save_1252)

test_plot_save_1252(BY_CHANNEL_1252[1], 
                    save_path = "../02_aggregated_data/dye_screen_tests",
                           add_to_canon = c("D23_TAMRA_protein"),
                           drop_from_canon = c("L18_FAM_protein"),
                    
                           add_to_noncanon = c("L18_FAM_protein"),
                           drop_from_noncanon = c("G2_FAM_protein", "H15_Cy5.5_protein", "L16_FAM_protein", "D23_TAMRA_protein"),
                    
                           add_to_SYPRO_canon = c(),
                           drop_from_SYPRO_canon = c(),
                    
                           add_to_SYPRO_noncanon = c(),
                           drop_from_SYPRO_noncanon = c()
                           )
```


########
Step 1: Assemble the hits-by-channel data for all dye screens. 

Exploration -- which directory has the final, tidiest version of this data?

Exp1216 -- original experiment where hits were called by channel. 
Neither the complete dataset nor the final, tidiest form
37 screens
```{r}
#### --- conclusion: not the final form
# most of these are done in Exp1216
BY_CHANNEL <- fs::dir_ls("/Users/taiaseanwu/Box Sync/data/Exp1216--20210902_aggregating_post_810_dye_screens/hits_by_channel", regexp = ".rds")
# length(BY_CHANNEL) # 37

screen <- read_rds(BY_CHANNEL[1])
# a few more are added in Exp

# a data structure where the channel rankings and data are in separate objects
# the assignments aren't present here either. 
str(screen)
# List of 2
#  $ ranked_channels: tibble [192 × 5] (S3: tbl_df/tbl/data.frame)
#   ..$ dye          : chr [1:192] "A003" "A003" "A003" "A003" ...
#   ..$ dye_channel_f: chr [1:192] "A003_FAM" "A003_JOE" "A003_TAMRA" "A003_ROX" ...
#   ..$ norm_auc     : num [1:192] 46.37 1.2 3.24 3.38 3.27 ...
#   ..$ auc_rank     : int [1:192] 6 1 3 5 4 2 5 4 6 3 ...
#   ..$ auc_hit      : chr [1:192] "fit" "drop" "drop" "drop" ...
#  $ hit_channels_df: gropd_df [13,440 × 10] (S3: grouped_df/tbl_df/tbl/data.frame)
#   ..$ variable        : chr [1:13440] "A1_FAM_protein" "A19_FAM_protein" "A20_FAM_protein" "A24_FAM_protein" ...
#   ..$ Temperature     : num [1:13440] 25 25 25 25 25 25 25 25 25 25 ...
#   ..$ value           : num [1:13440] 1036 7273 16513 28505 608 ...
#   ..$ dye_conc_uM     : num [1:13440] 10 50 50 50 50 50 50 50 50 50 ...
#   ..$ dye_channel_f   : chr [1:13440] "SYPRO_FAM" "C018_FAM" "C019_FAM" "T004_FAM" ...
#   ..$ type            : chr [1:13440] "protein" "protein" "protein" "protein" ...
#   ..$ value_norm      : num [1:13440] 0.386 0.99 1 1 0.55 ...
#   ..$ exp_num         : chr [1:13440] "Ds0005" "Ds0005" "Ds0005" "Ds0005" ...
#   ..$ identity        : chr [1:13440] "lysozyme" "lysozyme" "lysozyme" "lysozyme" ...
#   ..$ value_group_norm: num [1:13440] 0.578 0.99 1 1 0.574 ...
```

Exp1224 -- follow up experiment which called hits by channel.
Approaching the final, tidiest form, but not the complete dataset
38 screens (not the same as Exp1216, but I didn't )
```{r}
BY_CHANNEL_1224 <- fs::dir_ls("/Users/taiaseanwu/Box Sync/data/Exp1224--20211012_dye_screen_processing_gant_chart/processed_in_Exp1224/5_selected_for_fits/tidied_with_selections")

BY_CHANNEL_1224

length(BY_CHANNEL_1224) # [1] 38

screen <- read_rds(BY_CHANNEL_1224[1])
screen
```

##### scratch work below this line


```{r}
head(mtcars) |> 
  filter(mpg == 21 | disp == 225)
```

```{r}
dir_create("../02_aggregated_data/dye_screen_tests/SYPRO_canon")
```


```{r}
library(tidyverse)
library(fs)
library(testthat)
library(dsfworld)
source("R/tidy_dye_screen_from_Exp1216_read_and_clean_raw_screens.R") # for test_tidy_dye_scren() # TYPO IN FUNCTION NAME
  test_tidied_dye_screen <- test_tidied_dye_scren # correct the typo in the function name
source("R/choose_fit_channels.R")
```

Get directories for the raw data and assignments
```{r}
protein_order <-  c("Hsp72_SBD","p300_KIX","PPIEdeltaN","HisGB1","eIF2B_no_ISIB","eIF2B_with_ISRIB","kHvL_light_chain","Bag2","Hsc70","HIP","KaiC_AE","ACD_domain_protein6-","H104-FL-B5-pre-inc_protein5","FL-B5-pre-inc_protein2","B5_with_zinc","BSA","PPIE","NPAS2_PAS-A","PER2_PAS-AB_wt","CLOCK_PASB_W362A","BMAL1_PASB_W427A","HisPER2_AB_I324N","CBPKIX","HisSUMO","Hsp10","HisNusA","GS_WT","GS_R341C","GS_324S","GS_324C","B5-pre-inc_phosphomim_protein_4","nucleosome","Retinoic_acid_receptor_alpha","Widom_601_DNA","proteasome","nhr23_LBD")

raw_dirs <- fs::dir_ls("../lost_sheep/5_for_tma_extraction/tidied", regexp = ".rds")
assignment_dirs <- fs::dir_ls("../lost_sheep/5_for_tma_extraction/assignments/", regexp = ".rds")

### manual tests
# raw_dirs # screens appear in the same order in both
# assign_dirs # screens appear in the same order in both
names(raw_dirs) <- protein_order
names(assignment_dirs) <- protein_order

override_channels_df <- 
  readxl::read_excel("../lost_sheep/5_for_tma_extraction/channel_exceptions/Exp1224--20211011_channel_exceptions.xlsx") %>%
  filter(dye != "none") # these were placeholders so i knew i'd checked. 

### manual tests
# all proteins have matches
# all(override_channels_df$protein %in% protein_order)
```

Loop over all
```{r}
save_to <- "../processed_in_Exp1224/5_selected_for_fits/"
failed_screens <- list()
  for (i in c(1:length(raw_dirs))) { # for every raw screen to be fit
   
  ## generate names for saving and printing
    .protein <- names(raw_dirs[i])
   
    print(glue::glue("___________________{.protein}___________________"))
  
    # try({ 
      
      assigned_raw <-
          read_and_assign(raw_dirs[[i]],  # gets tested after reading
                            assignment_dirs[[i]])  # gets tested after reading
      
      # drop cases where a dye exists only in the buffer screen
      .keep_dyes <- 
        assigned_raw %>%
        filter(type == "protein") %>%
        pull(dye)
      
      prot_dyes_only <-
        assigned_raw %>%
        filter(dye %in% .keep_dyes)
      
      # add rankings
      ranked <-
        prot_dyes_only %>%
        rank_channels_1224()  %>%
        ungroup()
      
      print("starting if statement")
      if(.protein %in% override_channels_df$protein) {
        print("making override_channels")
         .override_channels <-
            override_channels_df %>%
            filter(protein == .protein) %>%
            unite(dye_channel_f, c(dye, fit_channel)) %>%
            pull(dye_channel_f) %>%
             unique()
         print("made override_chanels")
         
         ranked <- 
           ranked %>%
           update_channel_selections_1224(.ranked_df = .,
                                       .fit_dye_channels = .override_channels) %>%
        ungroup()
          print("make ranked")
      }


  print("Does updated tibble pass all tests?")
  if(all(test_ranked_channels(ranked))) {

  # save the updated tibble to a new folder
    save_filename <- get_save_name(raw_dirs[[i]])
    
    save_name <- glue::glue("{save_to}tidied_with_selections/{save_filename}")
    save_msg <- glue::glue("Saving screen with channel selections for fits to: '{save_filename}'")
    print(save_msg)
    write_rds(save_name, x = ranked)

    # also save the assignments with channel specifications, just in case we want this later
    rds_name_assign <- # modify name for this specific object
      save_filename %>% gsub(pattern = "tidied_with_fit_selections.rds",
                        replacement = "assignments_with_fit_selections.rds",
                        x = . )
    
    assign_df <- read_rds(assignment_dirs[[i]])
    
    ranked_assignments <-
      ranked %>%
      filter(fit_channel == "fit") %>%
      select(dye, channel_f) %>%
      distinct() %>%
      left_join(. , assign_df, by = "dye")

    save_name2 <- glue::glue("{save_to}assignments_with_selections/{rds_name_assign}")
    save_msg2 <- glue::glue("Saving assignments with channel selections for fits: '{save_name2}'")
    print(save_msg2)
    write_rds(save_name2, x = ranked_assignments)
  } 
  }
```






