---
title: "R Notebook"
output: html_notebook
---

Assemble standard SYPRO curves
Issue with previous Exp0794 was that I didn't save the expeirmental conditions, and I want to have them. 
```{r}
library(tidyverse)
library(fs)
library(testthat)
source("R/collect_dsf_data.R")

# styler::style_file(path = "01_seek_SYPRO_curves.Rmd")
```

Best option: look at the plots for the original data, filter out what you want, and then just use / plot that

In the end, I think it makes sense to load, clean, and label as I go
That way, I'll understand how much work each directory will be to include 
in the database
And I can stop at a reasonable time, instead of trying to get through an
unreasonable number of directories at the end. 

Tally the current state of the database
```{r}
tally_dsfbase()
```

Automated test for DSF data
```{r}
# test_plot_save # --- 
# test_dataset(dataset) 
# print_tallies
# save_plot_by_var
```

Exp0653 - SYPROlog testing. 
```{r}
### Read in initial file
Exp0653 <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp0653--21090719_AW_DSF_test_with_13_proteins/Exp0653--20190719_AW_13_proteins_DSF_test_protein_and_buffer_df_all_m.rds") |>
  unite(variable, c(well, channel_f), remove = FALSE) |>
  as_tibble() |>
  mutate(
    protein = replace_na(protein, "buffer"),
    id = "placeholder"
  ) |>
  select(
    id,
    well,
    Temperature,
    variable,
    value,
    channel_f,
    dye,
    conc,
    protein,
    type
  ) |>
  rename(dye_conc_uM = conc)

# separate the buffer values

# separate the SYPRO canon
Exp0653_SYPROlogs_canon <-
  Exp0653 |>
  filter(
    channel_f %in% c("JOE", "TAMRA", "ROX"),
    dye == "SYPRO",
    protein %in% c("PPIE")
  ) |>
  mutate(subset = "SYPRO_canon")

test_plot_save(Exp0653_SYPROlogs_canon)

# separate the SYPRO non-canon
Exp0653_SYPROlogs_noncanon <-
  Exp0653 |>
  filter(
    channel_f %in% c("JOE", "TAMRA", "ROX"),
    dye == "SYPRO",
    protein %in% c("BSA", "CLOCK_PASB", "NPAS2_AB")
  ) |>
  mutate(subset = "SYPRO_noncanon") |> 
  
  # manual removal
  filter(variable != "A9_ROX")

test_plot_save(Exp0653_SYPROlogs_noncanon)

############### SYPROLOG DATA #############
Exp0653_SYPROlogs_noncanon <-
  Exp0653 |>
  unite(protein_dye_channel,
    c(protein, dye, channel_f),
    sep = "-", remove = FALSE
  ) |>
  filter(protein_dye_channel %in% c(
    "BMAL1_PASB-AW-132-TAMRA",
    "BMAL1_PASB-AW-132-JOE",
    "BMAL1_PASB-AW-134-TAMRA",
    "BMAL1_PASB-AW-134-ROX",
    "BSA-AW-131-TAMRA",
    "BSA-AW-131-ROX",
    "BSA-AW-132-FAM",
    "BSA-AW-132-JOE",
    "BSA-AW-132-TAMRA",
    "BSA-AW-134-TAMRA",
    "CLOCK_PASB-AW-131-JOE",
    "CLOCK_PASB-AW-131-TAMRA",
    "CLOCK_PASB-AW-131-ROX",
    "CLOCK_PASB-AW-132-JOE",
    "CLOCK_PASB-AW-132-TAMRA",
    "CLOCK_PASB-AW-132-ROX",
    "FKBP12-AW-132-JOE",
    "FKBP12-AW-132-TAMRA",
    "FKBP12-AW-134-JOE",
    "FKBP12-AW-134-TAMRA",
    "HisPer2_I324N-AW-132-JOE",
    "HisPer2_I324N-AW-132-TAMRA",
    "HisPer2_I324N-AW-134-JOE",
    "HisPer2_I324N-AW-134-TAMRA",
    "HisPer2_I324N-AW-134-ROX",
    "PER2_PASAB-AW-132-TAMRA",
    "PER2_PASAB-AW-134-JOE",
    "PER2_PASAB-AW-134-TAMRA",
    "PER2_PASAB-AW-134-ROX"
  )) |>
  mutate(subset = "noncanon")

test_plot_save(Exp0653_SYPROlogs_noncanon)

# CANNON
Exp0653_SYPROlogs_canon <-
  Exp0653 |>
  unite(protein_dye_channel,
    c(protein, dye, channel_f),
    sep = "-", remove = FALSE
  ) |>
  filter(protein_dye_channel %in% c(
    "CLOCK_PASB-AW-134-JOE",
    "CLOCK_PASB-AW-134-TAMRA",
    "CLOCK_PASB-AW-134-ROX"
  )) |>
  mutate(subset = "canon")
test_plot_save(Exp0653_SYPROlogs_noncanon)
```

Exp0722 -  SYPRO with nanobodies
```{r}
Exp0722_nanobody_SYPRO <- read_csv("/Users/taiaseanwu/Box Sync/data/Exp0722--201910016_nanobody_DSF_with_Nick/raw/Exp0722-20191006_nick_nanobody_dsf_raw_data.csv") |> 
  pivot_longer(-Temperature, names_to = "well", values_to = "value") |> 
  mutate(col = tidyplate::get_well_col(well),
         row = tidyplate::get_well_row(well)) |>  
  mutate(protein = case_when(row == "A" ~ "buffer",
                             row == "B" ~ "Nb080",
                             row == "C" ~ "Nb01",
                             row == "D" ~ "Nb02",
                             row == "E" ~ "Nb03",
                             row == "F" ~ "Nb04",
                             row == "G" ~ "Nb05",
                             row == "H" ~ "Nb06",
                             row == "I" ~ "Nb07",
                             row == "J" ~ "Nb08",
                             row == "K" ~ "Nb09")) |> 
  select(-c(col, row)) |> 
  mutate(id = "placeholder",
         subset = "SYPRO_canon",
         variable = well,
         type = if_else(protein == "buffer",
                        true = "buffer",
                        false = "protein")
         ) |> 
  filter(Temperature != 95) |> # otherwise too long
  filter(!is.na(protein),
         protein != "buffer")

# from manaul inspection
noncanon <-  c("B1", "B2", "B3", "C2", "C3", "D2", "E2", "E3", "F2", "F3", "G3", "I1")

Exp0722_nanobody_SYPRO_canon <- 
    Exp0722_nanobody_SYPRO |> 
  filter(!well %in% noncanon) |> 
  mutate(subset = "SYPRO_canon")

Exp0722_nanobody_SYPRO_noncanon <-
  Exp0722_nanobody_SYPRO |> 
  filter(well %in% noncanon) |> 
  mutate(subset = "SYPRO_noncanon")

test_plot_save(Exp0722_nanobody_SYPRO_canon)
test_plot_save(Exp0722_nanobody_SYPRO_noncanon)
```

Exp0777
```{r}
Exp0777_paths <- c(
"/Users/taiaseanwu/Box Sync/data/Exp0777--20200124_repeat_thermocycling_dependence/Exp0777--20200124_repeat_thermocycling_ramp_rates_p25C_per_min_full_read/Exp0777--20200124_repeat_p25C_per_min_full_read -  Melt Curve RFU Results_FRET.csv",
"/Users/taiaseanwu/Box Sync/data/Exp0777--20200124_repeat_thermocycling_dependence/Exp0777--20200124_repeat_thermocycling_ramp_rates_p50C_per_minfull_read/Exp0777--20200124_repeat_thermocycling_ramp_rates_p50C_per_min -  Melt Curve RFU Results_FRET.csv",
"/Users/taiaseanwu/Box Sync/data/Exp0777--20200124_repeat_thermocycling_dependence/Exp0777--20200124_repeat_thermocycling_ramp_rates_1min_per_C_full_read/Exp0777--20200124_repeat_thermocycling_ramp_rates_1cpermin_full_read -  Melt Curve RFU Results_FRET.csv",
"/Users/taiaseanwu/Box Sync/data/Exp0777--20200124_repeat_thermocycling_dependence/Exp0777--20200124_repeat_thermocycling_ramp_rates_2min_per_C_full_read/Exp0777--20200124_repeat_thermocycling_ramp_rates_2C_per_min_full_read -  Melt Curve RFU Results_FRET.csv",
"/Users/taiaseanwu/Box Sync/data/Exp0777--20200124_repeat_thermocycling_dependence/Exp0777--20200124_repeat_thermocycling_ramp_rates_8min_per_C_full_read/Exp0777--20200124_repeat_thermocycling_ramp_rates_8min_per_C_full_read -  Melt Curve RFU Results_FRET.csv")

cycle_times <- c(0.25, 0.5, 1, 2, 8)

Exp0777_layout <- tidyplate::read_layout("/Users/taiaseanwu/Box Sync/data/Exp0777--20200124_repeat_thermocycling_dependence/Exp0777--20200124_repeat_thermocycling_dependence_layout_for-biorad-compatibility-figure.csv") |> 
  rename(protein = Protein, dye_conc_uM = SYPRO_conc) |> 
  mutate(id = "placeholder",
         type = "protein",
         variable = well,
         dye = "SYPRO")

read_Exp777 <- function(path, layout, cycle) {
   df <- read.csv(path) %>%
          .[-1] %>%
          gather(well, value, -Temperature) %>%
          merge(layout, by = 'well') %>%
         mutate( cycle = rep(cycle, times = nrow(.))) %>%
         as_tibble() |> 
        mutate(Temperature = as.numeric(Temperature)) |> 
       filter(Temperature != 95) |> 
       unite(variable, c(well, cycle), remove = FALSE) 
}

##### p25
p25_canon <- c("A1", "A2", "C1", "C2", "C3", "C5", "C6", "C7", "E1", "E2", "E3", "G1","G2", "G3", "I1", "I2", "I3", "K1", "K2", "K3", "O1", "O2", "O3")

p25_noncanon <- c("A5", "A6", "A7", "M1", "M2", "M3", "P1", "P2")

Exp0777_p25C_ramp_canon <- 
  read_Exp777(Exp0777_paths[[1]], layout = Exp0777_layout, cycle_times[[1]]) |> 
  mutate(subset = "SYPRO_canon") |> 
  ## manual removal of non-canon 
  filter(well %in% p25_canon)

test_plot_save(Exp0777_p25C_ramp_canon)

Exp0777_p25C_ramp_noncanon <- 
  read_Exp777(Exp0777_paths[[1]], layout = Exp0777_layout, cycle_times[[1]]) |> 
  mutate(subset = "SYPRO_noncanon") |> 
## manual removal of non-canon 
  filter(well %in% p25_noncanon)

test_plot_save(Exp0777_p25C_ramp_noncanon)

##### p5
p5_canon <- c("A1", "A2", "C1", "C2", "C3", "C5", "C6", "C7", "E1", "E2", "E3", "G1","G2", "G3", "I1", "I2", "I3", "K1", "K2", "K3", "O1", "O2", "O3")

p5_noncanon <- c("A5", "A6", "A7")

Exp0777_p5C_ramp_canon <- 
  read_Exp777(Exp0777_paths[[2]], layout = Exp0777_layout, cycle_times[[2]]) |> 
  mutate(subset = "SYPRO_canon") |> 
  ## manual removal of non-canon 
  filter(well %in% p5_canon)

test_plot_save(Exp0777_p5C_ramp_canon)

Exp0777_p5C_ramp_noncanon <- 
  read_Exp777(Exp0777_paths[[2]], layout = Exp0777_layout, cycle_times[[2]]) |> 
  mutate(subset = "SYPRO_noncanon") |> 
## manual removal of non-canon 
  filter(well %in% p5_noncanon)

test_plot_save(Exp0777_p5C_ramp_noncanon)

##### 1 min
min1_canon <- c("A1", "A2", "C1", "C2", "C3", "C5", "C6", "C7", "E1", "E2", "E3", "G1","G2", "G3", "I1", "I2", "I3", "K1", "K2", "K3", "O1", "O2", "O3")

min1_noncanon <- c("A5", "A6", "A7", "M1", "M2", "M3")

Exp0777_1min_ramp_canon <- 
  read_Exp777(Exp0777_paths[[3]], layout = Exp0777_layout, cycle_times[[3]]) |> 
  mutate(subset = "SYPRO_canon") |> 
  ## manual removal of non-canon 
  filter(well %in% min1_canon)

test_plot_save(Exp0777_1min_ramp_canon)

Exp0777_1min_ramp_noncanon <- 
  read_Exp777(Exp0777_paths[[3]], layout = Exp0777_layout, cycle_times[[3]]) |> 
  mutate(subset = "SYPRO_noncanon") |> 
## manual removal of non-canon 
  filter(well %in% min1_noncanon)

test_plot_save(Exp0777_1min_ramp_noncanon)

######## 2 min
min2_canon <- c("A1", "A2", "C1", "C2", "C3", "C5", "C6", "C7", "E1", "E2", "E3", "G1","G2", "G3", "I1", "I2", "I3", "K1", "K2", "K3", "O1", "O2", "O3")

min2_noncanon <- c("A5", "A6", "A7", "M1", "M2", "M3")

Exp0777_2min_ramp_canon <- 
  read_Exp777(Exp0777_paths[[4]], layout = Exp0777_layout, cycle_times[[4]]) |> 
  mutate(subset = "SYPRO_canon") |> 
  ## manual removal of non-canon 
  filter(well %in% min2_canon)

test_plot_save(Exp0777_2min_ramp_canon)

Exp0777_2min_ramp_noncanon <- 
  read_Exp777(Exp0777_paths[[4]], layout = Exp0777_layout, cycle_times[[4]]) |> 
  mutate(subset = "SYPRO_noncanon") |> 
## manual removal of non-canon 
  filter(well %in% min2_noncanon)

test_plot_save(Exp0777_2min_ramp_noncanon)

######## 8 min
min8_canon <- c("A1", "A2", "C1", "C2", "C3", "C5", "C6", "C7", "E1", "E2", "E3", "G1","G2", "G3", "I1", "I2", "I3", "K1", "K2", "K3", "O1", "O2", "O3")

min8_noncanon <- c("A5", "A6", "A7", "M1", "M2", "M3")

Exp0777_8min_ramp_canon <- 
  read_Exp777(Exp0777_paths[[5]], layout = Exp0777_layout, cycle_times[[5]]) |> 
  mutate(subset = "SYPRO_canon") |> 
  ## manual removal of non-canon 
  filter(well %in% min8_canon)

test_plot_save(Exp0777_8min_ramp_canon)

Exp0777_8min_ramp_noncanon <- 
  read_Exp777(Exp0777_paths[[5]], layout = Exp0777_layout, cycle_times[[5]]) |> 
  mutate(subset = "SYPRO_noncanon") |> 
## manual removal of non-canon 
  filter(well %in% min8_noncanon)

test_plot_save(Exp0777_8min_ramp_noncanon)
```

Exp0568_mAB from Dong Hee
```{r}
Exp0568_mAB_noncanon <- read_csv("/Users/taiaseanwu/Box Sync/data/Exp0568--20190508_DongHee_Data_Analysis/2019-05-02 14-15-43 C9 Tris different pH -  Melt Curve RFU Results_FRET_taia_trimmed_protein_only.csv") %>%
    pivot_longer(-Temperature, names_to = "well", values_to = "value") %>%
  mutate(protein = rep("mAB", nrow(.))) |> 
  mutate(id = "placeholder",
         subset = "SYPRO_noncanon",
         variable = well) |> 
  filter(Temperature == floor(Temperature),
         Temperature != 95) |> 
  mutate(row = tidyplate::get_well_row(well),
         col = tidyplate::get_well_col(well),
         pH = case_when(col %in% c(1, 6) ~ "pH6",
                        col %in% c(2, 7) ~ "pH7",
                        col %in% c(3, 8) ~ "pH8",
                        col %in% c(4, 9) ~ "pH9",
                        col %in% c(5, 10) ~ "pH7"),
          type = case_when(col %in% c(6,7,8,9,10) ~ "protein",
                        col %in% c(1,2,3,4,5) ~ "buffer"))
 
test_plot_save(Exp0568_mAB_noncanon)
```

Exp0790 CHIP ramp rates
```{r}
Exp0790_CHIP_MDH_peptides <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp0790--20200130_CHIP_70-5mer_MDH_ramp-rate-repeats/Exp0790--20200130_CHIP_70-5mer_MDH_ramp-rate-repeats_tidied.rds") |> 
  mutate(id = "placeholder") |> 
  as_tibble() |> 
  mutate(Temperature  = as.numeric(Temperature)) |> 
  mutate(variable = paste0(variable, "_", cycle)) |> 
  filter(Temperature != 95) |> 
  rename(protein = Protein,
         peptide = Peptide,
         peptide_conc_uM = Peptide_conc,
         protein_conc_uM = Protein_conc) |> 
  filter(protein != "Buffer") |> 
  select(-c(cycle_protein, cycle_protein_well, remove)) |> 
  filter(!cycle %in% c(1, 0.25, 4))

Exp0790_noncanon <- c("C5plateleft_0.5", "C5plateleft_2", "C5plateleft_8",
                      "C6plateleft_2","C6plateleft_8",
                      "C7plateleft_2", "C7plateleft_8")

Exp0790_CHIP_MDH_peptides_canon <-
  Exp0790_CHIP_MDH_peptides |> 
  mutate(subset = "SYPRO_canon") |> 
  filter(!variable %in% Exp0790_noncanon)

test_plot_save(Exp0790_CHIP_MDH_peptides_canon)

Exp0790_CHIP_MDH_peptides_noncanon <-
  Exp0790_CHIP_MDH_peptides |> 
  mutate(subset = "SYPRO_noncanon") |> 
  filter(variable %in% Exp0790_noncanon)

test_plot_save(Exp0790_CHIP_MDH_peptides_noncanon)
```


```{r}
Exp0827_nsp3_canon <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp0827--20200527_Nsp3_md_ADPribose_dose_response/for_Exp0879/Exp0827--processed_for_Exp0879.rds") |> 
  mutate(id = "placeholder",
         subset = "SYPRO_canon",
         protein = if_else(protein == "SP0148",
                           true = "nsp3_mac1",
                           false = protein)) |> 
  filter(protein != "Buffer",
         compound != "Empty",
         channel_f %in% c("JOE","TAMRA", "ROX")) 

Exp0827_nsp3_canon

test_plot_save(Exp0827_nsp3_canon)
```
```{r}
Exp0846_SYPRO <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp0846--20200714_Nsp3_fragment_hit_dose_response/for_Exp0879/Exp0846--processed_for_Exp0879.rds") |> 
  mutate(id = "placeholder",
         subset = "SYPRO_canon",
         protein = if_else(protein == "SP0148",
                           true = "nsp3_mac1",
                           false = protein)) |> 
  filter(protein == "nsp3_mac1",
         channel_f %in% c("TAMRA", "ROX"))

Exp0846_drop <- c("A11", "A12", "A9", "A7", "B12", "B9", "C12")
Exp0846_noncanon <- c("B7", "B11", "A6")

Exp0846_nsp3_canon <- Exp0846_SYPRO |> 
  filter(!well %in% c(Exp0846_drop, Exp0846_noncanon)) |> 
  mutate(subset = "SYPRO_canon")

test_plot_save(Exp0846_nsp3_canon)

Exp0846_nsp3_noncanon <- Exp0846_SYPRO |> 
  filter(well %in% Exp0846_noncanon)|> 
  mutate(subset = "SYPRO_noncanon")

test_plot_save(Exp0846_nsp3_noncanon)
```

```{r}
Exp0847_CHIP <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp0847--20200714_Matt_Callahan_CHIP_cyclic_pep_up_down_test/tidied_raw/Exp0847--20231101_Matt_Callahan_CHIP_cyclic_peptides.rds") |> 
   filter(Temperature != 95) |> 
    rename(peptide = Peptide,
         peptide_conc_uM = Peptide_conc_uM,
         protein_conc_uM = Protein_conc_uM) |> 
  mutate(id = "placeholder",
         subset = "SYPRO_canon",
         variable = well,
         protein = if_else(protein_conc_uM != 0, 
                           true = "CHIP",
                           false = "buffer"),
         type = if_else(protein_conc_uM != 0, 
                           true = "protein",
                           false = "buffer")) |> 
  select(-c("Peptide_index", "Peptide_not_cyclized", "Peptide_no_fraction", "Fraction_num", "Peptide_name", "Cyclized")) |> 
  filter(!is.na(condition),
         protein != "buffer")

Exp0847_CHIP_noncanon <- c("A12", "A3", "B3")

Exp0847_CHIP_canon <-
  Exp0847_CHIP |> 
  filter(!well %in% Exp0847_CHIP_noncanon) |> 
  mutate(subset = "SYPRO_canon")

test_plot_save(Exp0847_CHIP_canon)

Exp0847_CHIP_noncanon <-
  Exp0847_CHIP |> 
  filter(well %in% Exp0847_CHIP_noncanon) |> 
  mutate(subset = "SYPRO_noncanon")

test_plot_save(Exp0847_CHIP_noncanon)
```

```{r}
# Exp0839--20200714_Nsp3_screen_layout.csv
# Exp0849--20200715_Nsp3_purine_library_screen_20uM_plate1.csv
# Exp0849--20200715_Nsp3_purine_library_screen_20uM_plate2.csv
# Exp0849--20200715_Nsp3_purine_library_screen_20uM_plate3.csv
# Exp0849--20200715_Nsp3_purine_library_screen_20uM_plate4.csv

read_exp0849 <- function(path, layout){
  dsf <-  read_qtower( file_path = path) |> 
    left_join(layout, by = "well") |> 
    mutate(id = "placeholder",
           subset = "SYPRO_canon") |> 
    rename(protein = Protein,
           compound_class = Compound_class,
           compound_conc_uM = Compound_conc_uM,
           compound_unique = Compound_unique) |> 
    filter(channel_f %in% c("TAMRA"))
}


layout <- tidyplate::read_layout("/Users/taiaseanwu/Box Sync/data/Exp0849--20200715_Nsp3_purine_library_screen_20uM/raw/Exp0839--20200714_Nsp3_screen_layout.csv")

####### plate 1
Exp0849_nsp3_purine1 <- read_exp0849(layout  = layout, path = "/Users/taiaseanwu/Box Sync/data/Exp0849--20200715_Nsp3_purine_library_screen_20uM/raw/Exp0849--20200715_Nsp3_purine_library_screen_20uM_plate1.csv") 

purine1_gotcha <- c("P1", "P2", "O1", "N1", "M9", "M20", "M19", 
                    "M15", "M12", "L5", "L9", "L4", "L10", "L11", "L12", "L13", "L14", "L15", "L16", "L17", "L19","K3", "K21", "D3", "A14", "A15", "A16")

purine1_noncanon <- c("P8", "M7", "J8", "C12", "C10", "E12", "F18", "F6","J10" )

Exp0849_nsp3_purine1_canon <-
  Exp0849_nsp3_purine1 |> 
  mutate(subset = "SYPRO_canon") |> 
  filter(!well %in% c(purine1_gotcha, purine1_noncanon))

test_plot_save(Exp0849_nsp3_purine1_canon)

Exp0849_nsp3_purine1_noncanon <-
  Exp0849_nsp3_purine1 |> 
  mutate(subset = "SYPRO_noncanon") |> 
  filter(well %in% purine1_noncanon)

test_plot_save(Exp0849_nsp3_purine1_noncanon)

Exp0849_nsp3_purine1_gotcha <-
  Exp0849_nsp3_purine1 |> 
  mutate(subset = "gotcha") |> 
  filter(well %in% purine1_gotcha)

test_plot_save(Exp0849_nsp3_purine1_gotcha)

### there aer four other plates form this experiment, but i think we alreayd have enough  nsp3 representation here?

# plate2 <- read_qtower( screen_file = "/Users/taiaseanwu/Box Sync/data/Exp0849--20200715_Nsp3_purine_library_screen_20uM/raw/Exp0849--20200715_Nsp3_purine_library_screen_20uM_plate2.csv", 
#                        layout = layout, 
#                        plate_name = "plate2")
# 
# plate3 <- read_qtower( screen_file = "/Users/taiaseanwu/Box Sync/data/Exp0849--20200715_Nsp3_purine_library_screen_20uM/raw/Exp0849--20200715_Nsp3_purine_library_screen_20uM_plate3.csv", 
#                        layout = layout, 
#                        plate_name = "plate3")
# 
# plate4 <- read_qtower( screen_file = "/Users/taiaseanwu/Box Sync/data/Exp0849--20200715_Nsp3_purine_library_screen_20uM/raw/Exp0849--20200715_Nsp3_purine_library_screen_20uM_plate4.csv", 
#                        layout = layout, 
#                        plate_name = "plate4")
```

```{r}
tally_dsfbase()
```


Exp0920 - Nsp16/Nsp10 with SAM and Sinefungin

-- REMOVED THIS DATASET -- did a better job with adding Exp0920  in 03_add_canon
```{r}
# Exp0920 <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp0920--20201014_Nsp16_Nsp16-10_Nsp10_SAM_Sinefungin_p914/labeled/Exp0920_2020-10-15_Nsp16_Nsp1610_df_all.rds") |> 
#   mutate(id = "placeholder",
#          subset = "canon") |> 
#   unite(variable, c(well, channel_f), remove = FALSE) |> 
#   
#   # the most interesting curves -- see original experiment folder
#   filter(dye_channel %in%  c("L063_Cy5", "L063_Cy5.5", "A021_FAM", "A021_JOE","L091_TAMRA", "L091_ROX")) |> 
#   filter(!well %in% c("J12", "I5")) # noisy--not legit data
#   
# canon <- c("A12", "A16", "A4", "B16", "B4", "C16", "D16", "D4", "D24", "E16", "E4", "E24","G24", "I24", "I12","L12","L24","M12","F16", "F4", "G12", "G16", "G4", "H16", "H24", "H4", "I16", "J16", "J4", "K12", "K16", "K4", "L16", "L4", "M16", "N16", "N4")
#            
#            
# Exp0920_Nsp1610_canon <- 
#   Exp0920 |> 
#   filter(well %in% canon) |> 
#   mutate(subset = "canon")
# 
# test_plot_save(Exp0920_Nsp1610_canon)
# 
# Exp0920_Nsp1610_noncanon <- 
#   Exp0920 |> 
#   filter(!well %in% canon) |> 
#   mutate(subset = "noncanon")
# 
# test_plot_save(Exp0920_Nsp1610_noncanon)
```



```{r}
Exp0968 <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp0968--20201124_SP029_OGTase_with_UDP_up_down/analyzed/Exp0968_2020-11-26_df_all.rds") |> 
  mutate(id = "placeholder",
         subset = "canon") |> 
  filter(type == "protein") |> 
  unite(dye_channel, c(dye, channel_f), remove = FALSE) |> 
  unite(variable, c(well, channel_f), remove = FALSE)

noncanon <- c("A003_FAM", "A007_JOE", "A007_TAMRA", "A007_ROX",
              "A013_JOE", "A013_TAMRA", "A013_ROX", 
              "A014_Cy5", "A014_TAMRA", "A014_ROX",
               "A015_Cy5", "A015_Cy5.5",
               "A016_Cy5", "A016_Cy5.5",
              "A002_FAM",
              "A023_FAM", "A023_JOE","A023_TAMRA", "ROX",
              "A024_TAMRA", "A024_ROX",
              "AW131_TAMRA",
              "AW134_FAM",  "AW134_JOE",  "AW134_TAMRA",  "AW134_ROX", 
              "AW132_FAM",  "AW132_JOE",  "AW132_TAMRA",  "AW132_ROX", 
              "C018_FAM",
              "L062_TAMRA", "L062_ROX",
              "L062_Cy5", "L062_Cy5.5",
              "L089_FAM", "JOE", "L089_TAMRA", 
              "L090_JOE",
              "L091_FAM", "L091_JOE", "L091_TAMRA",
              "L094_ROX", "L094_Cy5", "L094_Cy5.5", 
              "L095_Cy5", "L095_Cy5.5", 
              "L097_Cy5", "L097_Cy5.5", 
              "L098_ROX", 
              "L099_ROX",
               "MWC007_ROX",
              "MWC061_JOE", "MWC061_TAMRA",
              "TW384_JOE", "TW384_TAMRA",
               "TW408_JOE", "TW408_TAMRA",
              "TW495_JOE", "TW495_TAMRA"
              )

drop <- c("A11_FAM", "B11_FAM", "C7_ROX", "C19_JOE", "C19_ROX", "C19_TAMRA", "C2_JOE", "C7_ROX", "D19_JOE", "E11_FAM", "F11_FAM", "I11_FAM", "J11_FAM", "K2_JOE", "M11_FAM", "N11_FAM", "N16_JOE", "N3_JOE")
canon <- c()

gotcha <- c("L093_FAM", "L093_TAMRA", "L093_JOE", "MWD16_TAMRA", "E11_TAMRA")

Exp0968_OGT_noncanon <-
  Exp0968 |> 
  filter(!variable %in% drop,
         dye_channel %in% noncanon) |> 
  mutate(subset = "noncanon")

Exp0968_OGT_gotcha <-
  Exp0968 |> 
  filter(!variable %in% drop,
         dye_channel %in% gotcha) |> 
  mutate(subset = "gotcha")

test_plot_save(Exp0968_OGT_gotcha)

tally_dsfbase()
```

Exp0938 PLPro
```{r}
Exp0938 <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp0983--20201202_PLPro_GRL0617_with_dyes/analyzed/SP198_PLPro_2020-12-03_df_all.rds") |> 
   mutate(id = "placeholder",
         subset = "canon") |> 
  mutate(type = if_else(protein == "PLPro",
                         true = "protein",
                         false = "buffer")) |> 
  filter(type == "protein") |> 
  unite(variable, c(well, channel_f), remove = FALSE)

SYPRO_canon <- c("SYPRO_JOE", "SYPRO_TAMRA")

canon <- c("L063_ROX", "L063_Cy5", "L063_Cy5.5", 
           "L093_JOE", "L093_TAMRA", "L093_ROX",
           "L095_Cy5", "L095_Cy5.5",
           "T004_FAM")
canon_variable <- c("A2_ROX","B2_ROX","C2_ROX")

noncanon <- c("A2_JOE", "A2_TAMRA", 
              "B2_JOE", "B2_TAMRA",
              "C2_JOE", "C2_TAMRA")

drop <- c("C5_FAM", "B1_ROX")
drop_well <- c("A2", "B2", "C2")

Exp0938_PLPro_canon <-
  Exp0938 |> 
  filter(!well %in% drop_well,
         !variable %in% drop, 
         dye_channel %in% canon) |> 
  mutate(subset = "canon")

test_plot_save(Exp0938_PLPro_canon)

Exp0938_PLPro_noncanon <-
  Exp0938 |> 
  filter(variable %in% noncanon) |> 
  mutate(subset = "noncanon")

test_plot_save(Exp0938_PLPro_noncanon)

Exp0938_PLPro_SYPRO_canon <-
  Exp0938 |> 
  filter(dye_channel %in% SYPRO_canon,
         !variable %in% c("C4_JOE", "C4_TAMRA")) |> 
  mutate(subset = "SYPRO_canon")

test_plot_save(Exp0938_PLPro_SYPRO_canon)
  
tally_dsfbase()
```



