---
title: "R Notebook"
output: html_notebook
---

Adding more non-SYPRO canon data

Want about another 500 or so, hopefully not all from the same few proteins..
<!-- tally_dsfbase() -->
<!-- 71 proteins and 1050 datasets in SYPRO cannon, -->
<!-- 52 proteins and 394 in cannon (not SYPRO), -->
<!-- 103 proteins and 1166 datasets in non-cannon -->

```{r}
tally_dsfbase()
library(glue)
library(tidyverse)
library(fs)
library(testthat)
library(glue) # for print messages
source("R/collect_dsf_data.R") 
source("R/dye_screens_to_dsfbase.R") # reading, tidy, process, plot, and add dye screens from Exp1252 to dsfbase
```

Helper function to print the variables so I can make 
reassignment vectors manually by copy-pasting
```{r}
print_quote <- function(vec, .sort_unique = TRUE){
  if(.sort_unique) {
    vec <- sort(unique(vec))
  }
  glue("{glue_collapse(double_quote(as.character(unique(vec))), sep = ', ')}")
}
```

Helper function to do some of the repetetive steps to prepare raw files for DSFbase 
```{r}
prep_dsfbase <- function(dsf,
                         .id = "placeholder",
                         .subset = "placeholder",
                         .buffer_name = "Buffer",
                         .add_variable = FALSE,
                         .add_variable_from = c("well", "channel_f")){
  dsf <- dsf |> 
   mutate(id = "placeholder",
         subset = "canon",
         type = if_else(protein != .buffer_name,
                        true = "protein",
                        false = "buffer")) |>
filter(protein != "Buffer") 
  
  if(.add_variable){
    dsf <- dsf |> 
      unite(variable, .add_variable_from, remove = FALSE)
  }
  
  dsf
  
}
```

Source: Exp1219 nsp3 with dye T004
- Exp1219_nsp3mac1_canon
- Exp1219_nsp3mac1_noncanon
```{r}
Exp1219_nsp3mac1 <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp1219--20211005_mac1_8539_analogs_set_1_DRC/intermediates/Exp1219--20211004_all_data_labeled.rds") |> 
 filter(channel_f == "FAM", 
        protein != "Buffer") |> 
  mutate(type = "protein") |> 
  mutate(id = "placeholder",
         subset = "placeholder")

# print_quote(sort(unique(Exp1219$variable)))
drop_from_all <- c( "E20_FAM_plate2", "E21_FAM_plate2","E22_FAM_plate2","E23_FAM_plate2", "E24_FAM_plate2","P1_FAM_plate1")

move_to_noncanon <- c("A23_FAM_plate2","B23_FAM_plate2","C23_FAM_plate2")

Exp1219_nsp3mac1_canon <- 
  Exp1219_nsp3mac1 |> 
  filter(!variable %in% drop_from_all,
         !variable %in% move_to_noncanon) |> 
  mutate(subset = "canon")
  
test_plot_save(Exp1219_nsp3mac1_canon)

Exp1219_nsp3mac1_noncanon <- 
  Exp1219_nsp3mac1 |> 
  filter(!variable %in% drop_from_all,
         variable %in% move_to_noncanon) |> 
  mutate(subset = "noncanon")

test_plot_save(Exp1219_nsp3mac1_noncanon)
```

Source: Exp1036 PLPro with GRL0617
- Exp1036_PLPro_GRL0617_canon
```{r}
# noisy data -- probably good to have some of that in here too 
Exp1036_PLPro_GRL0617_canon <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp1036--20201225_PLPro_L095_GRL0617_replicates/raw/Exp1036_2020-12-26_df_all.rds") |>

  # copied from Exp1036 notebook
  filter(dye != "Empty") |>
  mutate(across(c(GRL0617_conc), as.numeric)) |>
  select(-dye_conc_protein_channel) |>
  unite(variable, c(well, channel_f), remove = FALSE) |>
  unite(condition, c(channel_f, GRL0617_conc, conc), remove = FALSE) |>

  # dsfbase-specific
   mutate(id = "placeholder",
         subset = "canon",
         type = if_else(protein != "Buffer",
                        true = "protein",
                        false = "buffer")) |>
filter(protein != "Buffer",
       channel_f == "Cy5") 

test_plot_save(Exp1036_PLPro_GRL0617_canon)

Exp1036 |>
  ggplot(aes(x = Temperature,
             y = value,
             group = variable)) +
  geom_line() +
  facet_wrap(~channel_f)
```

Source: Exp1033 PLPro with GRL0617, up down and straight ramp
- Exp1033_PLPro_GRL0617_ud_canon
- Exp1033_PLPro_GRL0617_ud_noncanon
- Exp1033_PLPro_GRL0617_sr_noncanon
- Exp1033_PLPro_GRL0617_sr_canon
```{r}
## more good PLPro data

### up down mode
Exp1033_ud <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp1033--20201223_PLPro_GRL0617_ISG15/raw/Exp1033_up_down_2020-12-24_df_all.rds") |>
  prep_dsfbase(.add_variable = TRUE)  |> 
  group_by(variable) |> 
  filter(any(value > 10000),
         !dye_channel %in% c("L093_TAMRA", "L093_JOE", "L093_FAM", "L093_Cy5", "L093_Cy5.5"),
         !dye %in% c("L095")) |> 
  ungroup()

# following manual inspection
drop_variable <- c("G1_ROX", "H1_Cy5", "J1_Cy5.5", "J1_ROX", "K1_Cy5", "K1_Cy5.5", "K1_ROX", "K4_FAM", "L1_ROX", "L4_FAM", "I1_Cy5.5")

add_to_canon <- c("H2_ROX", "H5_FAM", "I2_ROX", "J4_FAM", "J4_JOE", "J4_ROX", "J4_TAMRA",
                  "K2_ROX", "L1_Cy5.5", "L2_ROX", "L5_FAM", "L4_ROX")

Exp1033_PLPro_GRL0617_ud_canon <- 
  Exp1033_ud |> 
  filter(variable %in% add_to_canon,
         !variable %in% drop_variable) |> 
  mutate(subset = "canon")

test_plot_save(Exp1033_PLPro_GRL0617_ud_canon)

Exp1033_PLPro_GRL0617_ud_noncanon <- 
  Exp1033_ud |> 
  filter(!variable %in% add_to_canon,
         !variable %in% drop_variable) |> 
  mutate(subset = "noncanon")

test_plot_save(Exp1033_PLPro_GRL0617_ud_noncanon)

### straight ramp
Exp1033_sr <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp1033--20201223_PLPro_GRL0617_ISG15/raw/Exp1033_straight_ramp_2020-12-24_df_all.rds") |> 
  prep_dsfbase(.add_variable = TRUE)  |> 
  group_by(variable) |> 
  filter(any(value > 10000)) |> 
  ungroup()

### L093 is non-canon
Exp1033_PLPro_GRL0617_sr_noncanon <- Exp1033_sr |> 
  filter(dye == "L093") |> 
  mutate(subset = "noncanon")

test_plot_save(Exp1033_PLPro_GRL0617_sr_noncanon)

## the rest are canon
Exp1033_PLPro_GRL0617_sr_canon <- Exp1033_sr |> 
  filter(dye != "L093",
         !variable %in% c("I5_FAM")) |> 
  mutate(subset = "canon")

test_plot_save(Exp1033_PLPro_GRL0617_sr_canon)

#tally_dsfbase()
```


Source: Nsp10 / Nsp16 SAM/Sinefungin 
- Exp0920_Nsp16_canon
- Exp0920_Nsp16_noncanon
- Exp0920_Nsp16_SYPRO_canon
```{r}
## look in the folder itself to get more guidance on the correct data to pull here
Exp0920 <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp0920--20201014_Nsp16_Nsp16-10_Nsp10_SAM_Sinefungin_p914/labeled/Exp0920--20201014_Nsp16_Nsp1610_Nsp10_SAM_Sinefungin_raw_data.rds") |> 
  mutate(id = "placeholder",
         subset = "placeholder",
         type = if_else(protein != "Buffer",
                        true = "protein",
                        false = "buffer")) |> 
  group_by(dye_conc_channel_f) |> 
  filter(any(value > 10000),
         protein != "Buffer") |> 
  ungroup()

# SP0181_Nsp16 SP0182_Nsp1610   SP0183_Nsp10 
#          29890          29890          29890 

#### Nsp16 with sinefungin
# print to help with selections
print_quote(Exp0920$dye_conc_channel_f)

Nsp16_canon <- c("L060_JOE 0.25", "L060_JOE 0.5", 
                            "A021_FAM 25", "A021_JOE 25", "A021_TAMRA 25", "A021_ROX 25",
                            "L091_JOE 25", "L091_TAMRA 25", "L091_ROX 25", "L098_ROX 25", 
                            "MWF08_FAM 25",
                            "A021_FAM 50",
                            "A021_FAM 50", "A021_JOE 50", "A021_TAMRA 50", "A021_ROX 50",
                            "L091_TAMRA 50", "L091_ROX 50",
                            "L097_Cy5 50", "L097_Cy5.5 50",
                            "MWF08_FAM 50",
                            "TW495_JOE 50", "TW495_TAMRA 50", "TW495_ROX 50"
                            )

### manual amendments
# print_quote(sort(Exp0920_Nsp16$variable))
drop_from_Nsp16_canon <- c("A6-JOE-SP0181_Nsp16", "A7-Cy5-SP0181_Nsp16","B12-JOE-SP0181_Nsp16", "B12-ROX-SP0181_Nsp16", "B12-TAMRA-SP0181_Nsp16", "B3-ROX-SP0181_Nsp16", "B4-JOE-SP0181_Nsp16", "C12-JOE-SP0181_Nsp16", "C12-TAMRA-SP0181_Nsp16","C4-TAMRA-SP0181_Nsp16", "C6-JOE-SP0181_Nsp16","C7-Cy5-SP0181_Nsp16","D6-JOE-SP0181_Nsp16","E12-FAM-SP0181_Nsp16",  "E4-TAMRA-SP0181_Nsp16", "E6-JOE-SP0181_Nsp16", "E7-Cy5-SP0181_Nsp16", "F6-JOE-SP0181_Nsp16", "G4-TAMRA-SP0181_Nsp16", "G6-JOE-SP0181_Nsp16", "G7-Cy5-SP0181_Nsp16", "H3-ROX-SP0181_Nsp16", "H4-JOE-SP0181_Nsp16","H6-JOE-SP0181_Nsp16","I4-TAMRA-SP0181_Nsp16", "I6-JOE-SP0181_Nsp16", "I7-Cy5-SP0181_Nsp16","J12-JOE-SP0181_Nsp16", "J12-TAMRA-SP0181_Nsp16", "J3-ROX-SP0181_Nsp16", "J4-JOE-SP0181_Nsp16","J6-JOE-SP0181_Nsp16", "K4-TAMRA-SP0181_Nsp16", "K6-JOE-SP0181_Nsp16", "K7-Cy5-SP0181_Nsp16","L4-JOE-SP0181_Nsp16", "M12-FAM-SP0181_Nsp16","M4-TAMRA-SP0181_Nsp16", "M6-JOE-SP0181_Nsp16", "M7-Cy5-SP0181_Nsp16", "N12-FAM-SP0181_Nsp16", "N12-JOE-SP0181_Nsp16", "N12-ROX-SP0181_Nsp16", "N12-TAMRA-SP0181_Nsp16", "N4-JOE-SP0181_Nsp16", "N6-JOE-SP0181_Nsp16")

add_to_Nsp16_noncanon <- c("A7-Cy5-SP0181_Nsp16","B12-JOE-SP0181_Nsp16", "B12-ROX-SP0181_Nsp16", "B12-TAMRA-SP0181_Nsp16", "B3-ROX-SP0181_Nsp16", "B4-JOE-SP0181_Nsp16", "C4-TAMRA-SP0181_Nsp16", "C6-JOE-SP0181_Nsp16","C7-Cy5-SP0181_Nsp16","D6-JOE-SP0181_Nsp16","E12-FAM-SP0181_Nsp16", "E6-JOE-SP0181_Nsp16", "E7-Cy5-SP0181_Nsp16", "F6-JOE-SP0181_Nsp16", "H3-ROX-SP0181_Nsp16", "H4-JOE-SP0181_Nsp16","H6-JOE-SP0181_Nsp16","I4-TAMRA-SP0181_Nsp16", "I6-JOE-SP0181_Nsp16", "I7-Cy5-SP0181_Nsp16","J6-JOE-SP0181_Nsp16",  "K6-JOE-SP0181_Nsp16", "K7-Cy5-SP0181_Nsp16", "M12-FAM-SP0181_Nsp16","M4-TAMRA-SP0181_Nsp16", "M6-JOE-SP0181_Nsp16", "M7-Cy5-SP0181_Nsp16", "N12-FAM-SP0181_Nsp16", "N12-JOE-SP0181_Nsp16", "N12-ROX-SP0181_Nsp16", "N12-TAMRA-SP0181_Nsp16",  "N6-JOE-SP0181_Nsp16")


Exp0920_Nsp16_canon <- Exp0920 |> 
  filter(protein == "SP0181_Nsp16",
         dye_conc_channel_f %in% Nsp16_canon,
         !variable %in% drop_from_Nsp16_canon) |> 
  group_by(variable) |> 
  filter(any(value > 10000)) |> 
  mutate(subset = "canon")

test_plot_save(Exp0920_Nsp16_canon)

#### Nsp16 noncanon

Nsp16_noncanon <- c("L063_Cy5 25", "L063_Cy5.5 25","L097_Cy5 25", "L097_Cy5.5 25",
                               "L098_Cy5 25", "L098_Cy5.5 25",
                               "TW495_JOE 25", "TW495_TAMRA 25", "TW495_ROX 25",
                               "AW134_JOE 50", "AW134_TAMRA 50")


Exp0920_Nsp16_noncanon <- Exp0920 |> 
  filter(protein == "SP0181_Nsp16",
         dye_conc_channel_f %in% Nsp16_noncanon | variable %in% add_to_Nsp16_noncanon) |> 
  group_by(variable) |> 
  filter(any(value > 10000)) |> 
  mutate(subset = "noncanon")

test_plot_save(Exp0920_Nsp16_noncanon)


#### Nsp16 SYPRO canon
Nsp16_SYPRO_canon <- c("SYPRO_JOE 25", "SYPRO_TAMRA 25", "SYPRO_ROX 25")

Exp0920_Nsp16_SYPRO_canon <- Exp0920 |> 
  filter(protein == "SP0181_Nsp16",
         dye_conc_channel_f %in% Nsp16_SYPRO_canon) |> 
  group_by(variable) |> 
  filter(any(value > 10000)) |> 
  mutate(subset = "SYPRO_canon")

test_plot_save(Exp0920_Nsp16_SYPRO_canon)
```

Source: Exp0920 Nsp1610 
- Exp0920_Nsp16Nsp10_SYPRO_canon
- Exp0920_Nsp16Nsp10_noncanon
- Exp0920_Nsp16Nsp10_canon
```{r}
# SP0181_Nsp16 SP0182_Nsp1610   SP0183_Nsp10 
#          29890          29890          29890 

#### Nsp16 with sinefungin
# print to help with selections
print_quote(Exp0920$dye_conc_channel_f)

## assume same as Nsp16 as first pass
Nsp16Nsp10_canon <- Nsp16_canon

# print_quote(sort(Exp0920_Nsp16Nsp10_canon$variable))
drop_from_Nsp16Nsp10_canon <- c("A19-Cy5-SP0182_Nsp1610", "A24-FAM-SP0182_Nsp1610", "A24-JOE-SP0182_Nsp1610", "A24-TAMRA-SP0182_Nsp1610", "B16-JOE-SP0182_Nsp1610", "B24-FAM-SP0182_Nsp1610", "B24-JOE-SP0182_Nsp1610", "B24-ROX-SP0182_Nsp1610", "B24-TAMRA-SP0182_Nsp1610",  "C19-Cy5-SP0182_Nsp1610", "C19-Cy5.5-SP0182_Nsp1610","C24-FAM-SP0182_Nsp1610", "C24-JOE-SP0182_Nsp1610", "C24-TAMRA-SP0182_Nsp1610","D18-JOE-SP0182_Nsp1610", "E18-JOE-SP0182_Nsp1610", "E19-Cy5-SP0182_Nsp1610", "E24-FAM-SP0182_Nsp1610","F16-TAMRA-SP0182_Nsp1610", "F24-FAM-SP0182_Nsp1610", "F18-JOE-SP0182_Nsp1610",
                        "G18-JOE-SP0182_Nsp1610", "G19-Cy5-SP0182_Nsp1610", "G24-FAM-SP0182_Nsp1610","H16-JOE-SP0182_Nsp1610","H18-JOE-SP0182_Nsp1610","I18-JOE-SP0182_Nsp1610", "I19-Cy5-SP0182_Nsp1610", "I24-FAM-SP0182_Nsp1610", "J16-JOE-SP0182_Nsp1610","J18-JOE-SP0182_Nsp1610","J24-JOE-SP0182_Nsp1610","J24-TAMRA-SP0182_Nsp1610",  "K18-JOE-SP0182_Nsp1610","K24-FAM-SP0182_Nsp1610", "L15-ROX-SP0182_Nsp1610", "L16-JOE-SP0182_Nsp1610", "L18-JOE-SP0182_Nsp1610", "L24-FAM-SP0182_Nsp1610","L24-JOE-SP0182_Nsp1610", "L24-ROX-SP0182_Nsp1610", "L24-TAMRA-SP0182_Nsp1610","M18-JOE-SP0182_Nsp1610","M24-FAM-SP0182_Nsp1610", "N15-ROX-SP0182_Nsp1610", "N16-JOE-SP0182_Nsp1610","N24-FAM-SP0182_Nsp1610", "N24-JOE-SP0182_Nsp1610", "N24-ROX-SP0182_Nsp1610", "N24-TAMRA-SP0182_Nsp1610")

add_to_Nsp16Nsp10_noncanon <- c("A19-Cy5-SP0182_Nsp1610", "A24-FAM-SP0182_Nsp1610", "A24-JOE-SP0182_Nsp1610", "A24-TAMRA-SP0182_Nsp1610",  "B24-FAM-SP0182_Nsp1610", "B24-JOE-SP0182_Nsp1610", "B24-ROX-SP0182_Nsp1610", "B24-TAMRA-SP0182_Nsp1610", "C19-Cy5-SP0182_Nsp1610", "C19-Cy5.5-SP0182_Nsp1610", "C24-FAM-SP0182_Nsp1610", "C24-JOE-SP0182_Nsp1610", "C24-TAMRA-SP0182_Nsp1610","D18-JOE-SP0182_Nsp1610", "E18-JOE-SP0182_Nsp1610", "E19-Cy5-SP0182_Nsp1610", "E24-FAM-SP0182_Nsp1610","F24-FAM-SP0182_Nsp1610",
  "G18-JOE-SP0182_Nsp1610", "G19-Cy5-SP0182_Nsp1610","F18-JOE-SP0182_Nsp1610", "G24-FAM-SP0182_Nsp1610","H18-JOE-SP0182_Nsp1610","I18-JOE-SP0182_Nsp1610", "I19-Cy5-SP0182_Nsp1610", "I24-FAM-SP0182_Nsp1610","J18-JOE-SP0182_Nsp1610", "K18-JOE-SP0182_Nsp1610","K24-FAM-SP0182_Nsp1610", "L24-FAM-SP0182_Nsp1610","L24-JOE-SP0182_Nsp1610", "L24-ROX-SP0182_Nsp1610", "L24-TAMRA-SP0182_Nsp1610","M18-JOE-SP0182_Nsp1610","M24-FAM-SP0182_Nsp1610", "N15-ROX-SP0182_Nsp1610", "N16-JOE-SP0182_Nsp1610","N24-FAM-SP0182_Nsp1610", "N24-JOE-SP0182_Nsp1610", "N24-ROX-SP0182_Nsp1610", "N24-TAMRA-SP0182_Nsp1610")

drop_from_Nsp16Nsp10_canon <- c(drop_from_Nsp16_canon, drop_from_Nsp16Nsp10_canon) #, Nsp16Nsp10_changes) # one change
add_to_Nsp16Nsp10_noncanon <- c(add_to_Nsp16_noncanon, add_to_Nsp16Nsp10_noncanon)
                                
Exp0920_Nsp16Nsp10_canon <- Exp0920 |> 
  filter(protein == "SP0182_Nsp1610",
         dye_conc_channel_f %in% Nsp16Nsp10_canon,
         !variable %in% drop_from_Nsp16Nsp10_canon) |> 
  group_by(variable) |> 
  filter(any(value > 10000)) |> 
  mutate(subset = "canon")

test_plot_save(Exp0920_Nsp16Nsp10_canon)

#### Nsp16 Nsp10 noncanon
Nsp16Nsp10_noncanon <- Nsp16_noncanon

Exp0920_Nsp16Nsp10_noncanon <- Exp0920 |> 
  filter(protein == "SP0182_Nsp1610",
         dye_conc_channel_f %in% Nsp16Nsp10_noncanon | variable %in% add_to_Nsp16Nsp10_noncanon) |> 
  group_by(variable) |> 
  filter(any(value > 10000)) |> 
  mutate(subset = "noncanon")

test_plot_save(Exp0920_Nsp16Nsp10_noncanon)


#### Nsp16 SYPRO canon
Nsp16Nsp10_SYPRO_canon <- c("SYPRO_JOE 25", "SYPRO_TAMRA 25", "SYPRO_ROX 25")
# drop_from_Nsp16Nsp10_SYPRO_canon <- c("H1-JOE-SP0181_Nsp16", "H1-TAMRA-SP0181_Nsp16", "J1-JOE-SP0181_Nsp16", "J1-TAMRA-SP0181_Nsp16")

Exp0920_Nsp16Nsp10_SYPRO_canon <- Exp0920 |> 
  filter(protein == "SP0182_Nsp1610",
         dye_conc_channel_f %in% Nsp16Nsp10_SYPRO_canon) |> 
  group_by(variable) |> 
  filter(any(value > 10000)) |> 
  mutate(subset = "SYPRO_canon")

test_plot_save(Exp0920_Nsp16Nsp10_SYPRO_canon)

# tally_dsfbase()
# 73 proteins and 1080 datasets in SYPRO cannon,
# 58 proteins and 893 in cannon (not SYPRO),
# 106 proteins and 1450 datasets in non-cannon
```

Source: Exp1106 -- OGT, OTL, and TPR with UDP GlcNAc and peptides
- Exp1106_OGT_noncanon
- Exp1106_TPR_canon
- Exp1106_OTL_canon
```{r}
Exp1106 <- 
  read_rds("/Users/taiaseanwu/Box Sync/data/Exp1106--20210305_OGT_OTL_TPR_peptide_tests/intermediate/Exp1106--20210305__OGT_OTL_TPR_M11_and_HCF1_peptides_df_all.rds") |> 
  mutate(id = "placeholder",
         subset = "placeholder",
         type = if_else(protein != "Buffer",
                        true = "protein",
                        false = "buffer")) |> 
  filter(peptide != "Ph21_long", 
         protein != "Buffer",
         channel_f %in% c("FAM", "JOE", "TAMRA", "ROX")) 

### add OGT to noncanon because it has two transitions
Exp1106_OGT_noncanon <- Exp1106 |> 
  filter(protein == "SP029_OGT") |> 
  mutate(subset = "noncanon")

test_plot_save(Exp1106_OGT_noncanon)

### add TPR to canon
Exp1106_TPR_canon <- Exp1106 |> 
  filter(protein == "SP207_TPR",
         channel_f %in% c("JOE", "TAMRA")) |>  # TPR signal lower than OGT
  mutate(subset = "canon")

test_plot_save(Exp1106_TPR_canon)


### add OTL to canon
Exp1106_OTL_canon <- Exp1106 |> 
  filter(protein == "SP206_OTL",
         channel_f %in% c("JOE", "TAMRA")) |>  # OTL signal lower than OGT
  mutate(subset = "canon")

test_plot_save(Exp1106_OTL_canon)
```

Source: Exp1101 -- OTL and TPR with L3Pra
- Exp1101_TPR_canon
- Exp1101_OTL_canon
```{r}
# test_plot_save(Exp0653_SYPROlogs_noncanon)

### might all be SYPRO data, but still good and beautiful SYPRO data
Exp1101 <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp1101--20210301_OGT_OTL_TPR_mixes_UDP_L3Pra/intermediates/Exp1101--20210301_OTL_TPR_mixtures_UDP_L3Pra_raw.rds") |> 
 mutate(id = "placeholder",
         subset = "placeholder",
         type = if_else(protein != "Buffer",
                        true = "protein",
                        false = "buffer")) |> 
  filter(protein != "Buffer",
         channel_f %in% c("FAM", "JOE", "TAMRA", "ROX")) 



### add TPR to canon
Exp1101_TPR_canon <- Exp1101 |> 
  filter(protein == "SP207_TPR") |>  # TPR signal lower than OGT
  mutate(subset = "canon")

test_plot_save(Exp1101_TPR_canon)


### add OTL to canon
Exp1101_OTL_canon <- Exp1101 |> 
  filter(protein == "SP206_OTL") |>  # OTL signal lower than OGT
  mutate(subset = "canon")

test_plot_save(Exp1101_OTL_canon)

```

Function to prepare valdiation screens for plotting
```{r}
prep_validation <- function(validation_raw, min_value = 10000) {
  validation_raw |> 
    mutate(id = "placeholder",
           subset = "placeholder") |> 
    rename(dye_conc_uM = conc) |>
    select(-volume) |>
    mutate(type = if_else(protein != "Buffer",
                          true = "protein",
                          false = "buffer")) |>
    filter(type == "protein") |>
    unite(variable, c(well, channel_f, protein), remove = FALSE) |>
    group_by(variable) |>
    filter(any(value > min_value)) |>
    ungroup()
    
}
```

Source: validations

Source: Exp1103 - Nsp10 validation
- Exp1103_Nsp10_canon
- Exp1103_Nsp10_noncanon
```{r}
Exp1103 <- read_rds("/Users/taiaseanwu/Box Sync/data/dye_screens/Exp1103--20210303_SP200-ISG15_SP186-Nsp10_validation_repeat/SP186_Nsp10/Exp1103_SP186_Nsp10_validation_2021-03-03_df_all.rds") |> 
  prep_validation() |> 
  mutate(subset = "placeholder")

# print_quote(sort(unique(Exp1103$variable)))
drop <- c("A1_JOE_SP186_Nsp10", "A1_TAMRA_SP186_Nsp10", "A10_JOE_SP186_Nsp10", "A10_TAMRA_SP186_Nsp10",  "A7_FAM_SP186_Nsp10","A9_JOE_SP186_Nsp10", "A9_TAMRA_SP186_Nsp10", "C1_JOE_SP186_Nsp10","C1_TAMRA_SP186_Nsp10", "C10_FAM_SP186_Nsp10", "C10_JOE_SP186_Nsp10", "C10_TAMRA_SP186_Nsp10", "C9_JOE_SP186_Nsp10", "C9_ROX_SP186_Nsp10", "C9_TAMRA_SP186_Nsp10", "E1_FAM_SP186_Nsp10", "E6_FAM_SP186_Nsp10",  "E8_TAMRA_SP186_Nsp10", "E9_JOE_SP186_Nsp10", "E9_TAMRA_SP186_Nsp10", "G1_JOE_SP186_Nsp10", "C14_FAM_SP186_Nsp10", "C4_JOE_SP186_Nsp10", "C4_ROX_SP186_Nsp10", "C6_FAM_SP186_Nsp10", "C7_FAM_SP186_Nsp10", "G1_TAMRA_SP186_Nsp10","G6_FAM_SP186_Nsp10", "G7_FAM_SP186_Nsp10", "G9_JOE_SP186_Nsp10", "G9_TAMRA_SP186_Nsp10")

add_to_noncanon <-c("A1_FAM_SP186_Nsp10","A1_ROX_SP186_Nsp10", "A11_JOE_SP186_Nsp10", "A11_ROX_SP186_Nsp10", "A11_TAMRA_SP186_Nsp10","A4_JOE_SP186_Nsp10", "A4_ROX_SP186_Nsp10", "A4_TAMRA_SP186_Nsp10","A6_FAM_SP186_Nsp10", "A8_JOE_SP186_Nsp10", "A8_TAMRA_SP186_Nsp10", "A9_Cy5_SP186_Nsp10",  "C1_FAM_SP186_Nsp10", "C1_ROX_SP186_Nsp10", "C11_JOE_SP186_Nsp10", "C11_TAMRA_SP186_Nsp10","C4_TAMRA_SP186_Nsp10", "C8_TAMRA_SP186_Nsp10",  "E10_FAM_SP186_Nsp10", "E10_JOE_SP186_Nsp10", "E10_TAMRA_SP186_Nsp10", "E11_JOE_SP186_Nsp10", "E11_TAMRA_SP186_Nsp10", "E4_JOE_SP186_Nsp10", "E4_ROX_SP186_Nsp10", "E4_TAMRA_SP186_Nsp10",  "E7_FAM_SP186_Nsp10", "G1_FAM_SP186_Nsp10",  "G1_ROX_SP186_Nsp10", "G10_JOE_SP186_Nsp10", "G10_TAMRA_SP186_Nsp10", "G11_JOE_SP186_Nsp10", "G11_TAMRA_SP186_Nsp10","G4_JOE_SP186_Nsp10", "G4_ROX_SP186_Nsp10", "G4_TAMRA_SP186_Nsp10", "G5_Cy5_SP186_Nsp10","G9_Cy5_SP186_Nsp10", "G9_Cy5.5_SP186_Nsp10")

Exp1103_Nsp10_canon <- Exp1103 |> 
  filter(!variable %in% add_to_noncanon,
         !variable %in% drop) |> 
  mutate(subset = "canon")

test_plot_save(Exp1103_Nsp10_canon)

Exp1103_Nsp10_noncanon <- Exp1103 |> 
  filter(variable %in% add_to_noncanon) |> 
  mutate(subset = "noncanon")

test_plot_save(Exp1103_Nsp10_noncanon)

```

Source: Exp1103 - ISG15 validation
- Exp1103_ISG15_noncanon
- Exp1103_ISG15_canon
```{r}
Exp1103_ISG15 <- read_rds("/Users/taiaseanwu/Box Sync/data/dye_screens/Exp1103--20210303_SP200-ISG15_SP186-Nsp10_validation_repeat/SP200_ISG15/Exp1103_SP200_ISG15_validation_2021-03-03_df_all.rds") |> 
  prep_validation(min_value = 5000) |> 
  mutate(subset = "placeholder") |> 
  filter(dye_channel %in% c("A016_Cy5", "A016_Cy5.5",
                            "C019_FAM",
                            "L091_JOE", "L091_TAMRA", "L091_ROX",
                            "L094_ROX", "L094_Cy5",
                            "L097_Cy5",
                            "T004_FAM",
                            "TW408_JOE", "TW408_TAMRA", "TW408_ROX"))

# print_quote(sort(unique(Exp1103_ISG15_canon$variable)))
drop <- c("A21_FAM_SP200_ISG15", "C21_FAM_SP200_ISG15", "G24_FAM_SP200_ISG15")
keep_in_canon<- c("E21_FAM_SP200_ISG15","G21_FAM_SP200_ISG15","G19_ROX_SP200_ISG15", "G19_TAMRA_SP200_ISG15", "E19_ROX_SP200_ISG15", "C22_Cy5_SP200_ISG15")

Exp1103_ISG15_noncanon <- Exp1103_ISG15 |> 
  filter(!variable %in% c(drop, keep_in_canon)) |> 
  mutate(subset = "noncanon")  
  
test_plot_save(Exp1103_ISG15_noncanon)

Exp1103_ISG15_canon <- Exp1103_ISG15 |> 
  filter(variable %in% c(keep_in_canon)) |> 
  mutate(subset = "canon")  
  
test_plot_save(Exp1103_ISG15_canon)
```



```{r}
tally_dsfbase()
# 73 proteins and 1080 datasets in SYPRO cannon,
# 62 proteins and 1324 in cannon (not SYPRO),
# 109 proteins and 1480 datasets in non-cannon
```

------------  Ferroportin 1 data directory
Source: Exp1021 FPN with MWF08 and hepcidin DRC
- Exp1021_FPN_canon
- Exp1021_FPN_noncanon
```{r}
Exp1021 <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp1051--20210105_FPN_meeting_1/data/Exps_to_date/Exp1021--20201218_SP203_FPN_MWF08_hepcidin/processed_screen/Exp1021_2020-12-19_df_all.rds") |> 
  prep_dsfbase(.add_variable = TRUE) |> 
  group_by(variable) |> 
  filter(any(value > 5000)) |> 
  ungroup() |> 
  rename(dye_conc_uM = conc) |> 
  mutate(subset = "canon")


Exp1021_FPN_canon <- Exp1021 |> 
  filter(channel_f == "FAM") 

test_plot_save(Exp1021_FPN_canon)

Exp1021_FPN_noncanon <- Exp1021 |> 
  filter(channel_f == "TAMRA") |> 
  mutate(subset = "noncanon")

test_plot_save(Exp1021_FPN_noncanon)
```

Other possible FPN directories
```{r}
# option -- some MWF08 data
# "/Users/taiaseanwu/Box Sync/data/Exp1051--20210105_FPN_meeting_1/data/Exps_to_date/Exp1021--20201218_SP203_FPN_MWF08_hepcidin/processed_screen/Exp1021_2020-12-19_df_all.rds"

# option -- some validation data with nanodiscs
# "/Users/taiaseanwu/Box Sync/data/Exp1129--20210422_FPN_detective_work_when_did_stuff_stop_working/data/Exp1022--20201219_SP203_SP204_FPN_LMNG_nanodisc_validation/processed_screen/Exp1022_FPN_2020-12-20_df_all.rds"

# option -- up down screen
# "/Users/taiaseanwu/Box Sync/data/Exp1051--20210105_FPN_meeting_1/data/Exps_to_date/Exp1025--20201219_SP204_FPN_nanodisc_up_down_dye_screen_1023/processed_screen/Exp1025_2020-12-20_df_all.rds"

# potential best option -- from shape classes. but this might be over-processed...?
# "/Users/taiaseanwu/Box Sync/data/Exp1129--20210422_FPN_detective_work_when_did_stuff_stop_working/data/Exp1042--20201230_FPN_nanodisc_shape_class_next_step_planning/raw/Exp1025_2020-12-20_df_all.rds"

## other good option -- up down validation

# "/Users/taiaseanwu/Box Sync/data/Exp1254--20211208_figure3c_FPN_and_nuc_highlights/input_data/FPN/with_best_dyes/Exps_to_date/Exp1049--20210102_FPN_ND_up_down_validation/analyzed_screens/Exp1049_2021-01-03_df_all.rds"
# "/Users/taiaseanwu/Box Sync/data/Exp1254--20211208_figure3c_FPN_and_nuc_highlights/input_data/FPN/with_best_dyes/Exps_to_date/Exp1049--20210102_FPN_ND_up_down_validation/analyzed_screens/Exp1049_2021-01-03_manually_called_hits.csv"

## up down wit hcompoujnds -- see notebook for definiton of best dyes
# "/Users/taiaseanwu/Box Sync/data/Exp1254--20211208_figure3c_FPN_and_nuc_highlights/input_data/FPN/with_best_dyes/Exp1059--20210118_FPN_up_down_with_compounds/raw/Exp1059_2021-01-21_df_all.rds"


## with compounds, only maybe worth putting in
# "/Users/taiaseanwu/Box Sync/data/Exp1129--20210422_FPN_detective_work_when_did_stuff_stop_working/data/Exp1084--20210212_FPN_ND_with_compounds_repeat_no_incubation/raw/Exp1084_FPN_with_compounds_2021-02-25_df_all.rds"


## wit hcompounds -- worth looking at again
# "/Users/taiaseanwu/Box Sync/data/Exp1084--20210212_FPN_ND_with_compounds_repeat_no_incubation/raw/Exp1084_FPN_with_compounds_2021-02-25_df_all_reformatted.rds"


```

Source: 
```{r}
# from manual inspection of original experiment plots, keep these
keep_LMNG <- c("L062_Cy5", "L062_Cy5.5", "MWF08_FAM", "T004_FAM")
keep_nanodisc <- c("A023_TAMRA", "A023_ROX", "MWC007_ROX", "MWF08_FAM") 

Exp1022 <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp1129--20210422_FPN_detective_work_when_did_stuff_stop_working/data/Exp1022--20201219_SP203_SP204_FPN_LMNG_nanodisc_validation/processed_screen/Exp1022_FPN_2020-12-20_df_all.rds") |>
  prep_dsfbase(.add_variable = TRUE) |> 
  filter(protein %in% c("SP203_FPN_LMNG", "SP204_FPN_nanodisc")) |> 
  group_by(variable) |> 
  filter(any(value > 5000)) |> 
  ungroup() |> 
  filter(case_when(protein == "SP203_FPN_LMNG" ~ dye_channel %in% keep_LMNG,
                   T ~ dye_channel %in% keep_nanodisc)) |> 
  rename(dye_conc_uM = conc) |> 
  mutate(subset = "canon") 

#print_quote(Exp1022$variable)
drop <- c("A15_ROX", "A15_TAMRA","B11_Cy5", "B11_Cy5.5", "B14_FAM", "B15_ROX", "B15_TAMRA", "C14_FAM", "C15_ROX", "D11_Cy5", "D11_Cy5.5", "D14_FAM", "D15_ROX","D18_ROX",  "E11_Cy5", "E11_Cy5.5", "E14_FAM", "E15_ROX",  "F11_Cy5", "F11_Cy5.5","F15_ROX", "F15_TAMRA",  "G14_FAM", "H14_FAM", "H15_ROX", "H15_TAMRA",  "H20_FAM", "I13_FAM", "I14_FAM", "I15_ROX", "I15_TAMRA", "I20_FAM", "J11_Cy5", "J11_Cy5.5", "J13_FAM", "J14_FAM", "J15_ROX", "J15_TAMRA", "J20_FAM", "K11_Cy5", "K11_Cy5.5", "K13_FAM", "K14_FAM", "K15_ROX", "K15_TAMRA", "K20_FAM", "L11_Cy5", "L11_Cy5.5", "L13_FAM", "L14_FAM", "L15_ROX", "L15_TAMRA", "L20_FAM", "H11_Cy5", "H11_Cy5.5")

canon <- c("A13_FAM","A20_FAM", "B13_FAM",  "B20_FAM","C13_FAM","D13_FAM",  "D20_FAM","E13_FAM", "E20_FAM", "F13_FAM","F20_FAM",  "G13_FAM", "G20_FAM", "H13_FAM", "C20_FAM")

gotcha <- c("A11_Cy5", "A11_Cy5.5", "A14_FAM",  "F14_FAM")


Exp1022_FPN_canon <- Exp1022 |> 
  filter(variable %in% canon) |> 
  mutate(subset = "canon")

test_plot_save(Exp1022_FPN_canon)

Exp1022_FPN_noncanon <- Exp1022 |> 
  filter(!variable %in% c(drop, gotcha, canon)) |> 
  mutate(subset = "noncanon")

test_plot_save(Exp1022_FPN_noncanon)

Exp1022_FPN_gotcha <- Exp1022 |> 
  filter(variable %in% gotcha) |> 
  mutate(subset = "gotcha")

# tally_dsfbase()
# 73 proteins and 1080 datasets in SYPRO cannon,
# 65 proteins and 1389 in cannon (not SYPRO),
# 112 proteins and 1542 datasets in non-cannon
```

Source: 
```{r}
Exp1030_nsp3mac1_canon <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp1192--20210713_nsp3_compound_sensitivity_by_dye_repeat/Exp1030--20201224_Nsp3_mac1_validation_SR_and_UD/analyzed_screen/straight_ramp/Exp1030--Nsp3_mac1_validation_straight_ramp_2020-12-25_df_all.rds") |> 
  prep_validation(min_value = 3000) |> 
  filter(dye_channel %in% c("L063_ROX","L063_Cy5", "L063_Cy5.5",
                            "L091_TAMRA",
                            "L093_ROX",
                            "L094_Cy5",
                            "L094_ROX",
                            "L096_ROX",
                            "L097_Cy5", "L097_Cy5.5",
                            "L098_ROX",
                            "T004_FAM",
                            "TW408_JOE",
                            "TW408_TAMRA",
                            "TW408_ROX"
                            ),
         !variable %in% drop) |> 
  mutate(subset = "canon") 
# print_quote(Exp1030$variable)
drop <- c("A10_Cy5_SP150_Nsp3_mac1", "A10_ROX_SP150_Nsp3_mac1", "A15_FAM_SP150_Nsp3_mac1",  "A6_Cy5_SP150_Nsp3_mac1", "A8_TAMRA_SP150_Nsp3_mac1", "A9_ROX_SP150_Nsp3_mac1", "B10_Cy5_SP150_Nsp3_mac1", "B10_ROX_SP150_Nsp3_mac1", "B11_ROX_SP150_Nsp3_mac1","B15_FAM_SP150_Nsp3_mac1", "B8_TAMRA_SP150_Nsp3_mac1", "B9_ROX_SP150_Nsp3_mac1", "C10_Cy5_SP150_Nsp3_mac1", "C10_ROX_SP150_Nsp3_mac1", "C11_ROX_SP150_Nsp3_mac1", "C15_FAM_SP150_Nsp3_mac1","C16_JOE_SP150_Nsp3_mac1", "C16_ROX_SP150_Nsp3_mac1", "C16_TAMRA_SP150_Nsp3_mac1","C8_TAMRA_SP150_Nsp3_mac1", "C9_ROX_SP150_Nsp3_mac1", "D10_Cy5_SP150_Nsp3_mac1", "D10_ROX_SP150_Nsp3_mac1", "D11_ROX_SP150_Nsp3_mac1","D8_TAMRA_SP150_Nsp3_mac1", "D9_ROX_SP150_Nsp3_mac1")


test_plot_save(Exp1030_nsp3mac1_canon)

tally_dsfbase()
```

Source: nsp2
```{r}
# nsp2 validation
Exp1142 <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp1142--20210430_nsp2_with_zinc_repeat/intermediate/Exp1142--20210403_nsp2_with_zinc_repeat_df_all.rds") |> 
  prep_dsfbase() |>
  rename(dye = compound,
         dye_conc_uM = concentration) |> 
  unite(dye_channel, c(dye, channel_f), remove = FALSE) |> 
  filter(dye_channel %in% c("A010_JOE", "A010_TAMRA",
                            "L062_Cy5", "L062_Cy5.5",
                            "L063_Cy5", "L063_Cy5.5",
                            "L093_ROX",
                            "L094_ROX","L094_Cy5","L094_Cy5.5",
                            "MWF08_FAM",
                            "T004_FAM",
                            "TW408_FAM", "TW408_JOE", "TW408_TAMRA", "TW408_ROX")
    
  ) |> 
  mutate(subset = "canon")

print_quote(Exp1142$variable)
noncanon <- c("A12_Cy5", "A12_Cy5.5", "A13_Cy5", "A13_Cy5.5", "A14_Cy5", "A14_Cy5.5",  "A15_ROX", "A16_FAM", "A3_Cy5", "A3_Cy5.5","C11_ROX","C12_Cy5.5", "C13_Cy5", "C13_Cy5.5","C3_Cy5", "C3_Cy5.5", "C4_Cy5", "C4_Cy5.5", "C5_Cy5", "C5_Cy5.5", "C5_ROX", "C6_ROX", "C7_FAM", "C9_TAMRA", "E11_FAM", "E11_JOE","E11_TAMRA", "E13_Cy5", "E13_Cy5.5", "E14_Cy5", "E14_Cy5.5", "E14_ROX", "E2_JOE",  "E4_Cy5", "E4_Cy5.5",  "G11_FAM",  "G12_Cy5", "G12_Cy5.5", "G13_Cy5", "G13_Cy5.5", "G14_Cy5", "G14_Cy5.5", "G14_ROX", "G15_ROX", "G16_FAM","G18_TAMRA", "G2_TAMRA", "G4_Cy5", "G4_Cy5.5", "G5_ROX", "G6_ROX", "G7_FAM",   "I11_ROX","I13_Cy5", "I13_Cy5.5","I16_FAM", "K14_Cy5", "K14_Cy5.5", "K14_ROX", "K15_ROX", "K16_FAM", "M11_FAM", "M11_JOE", "M11_ROX", "M11_TAMRA", "M13_Cy5", "M13_Cy5.5",  "O11_FAM", "O11_JOE",  "O11_TAMRA", "O12_Cy5", "O12_Cy5.5", "O13_Cy5", "O13_Cy5.5", "O14_Cy5", "O14_ROX")

drop <- c( "A4_Cy5", "A4_Cy5.5","A5_Cy5.5", "A5_ROX", "A6_ROX", "A7_FAM",  "A9_JOE","C14_ROX",  "C15_ROX", "C16_FAM",  "C18_JOE", "C18_TAMRA","C2_ROX","C9_JOE","E11_ROX","E15_ROX", "E16_FAM",  "E2_ROX", "E2_TAMRA", "E5_Cy5", "E5_Cy5.5", "E5_ROX", "E6_ROX", "G11_JOE", "G11_ROX", "G11_TAMRA","G17_FAM", "G18_JOE", "G2_FAM", "G2_JOE", "G2_ROX", "G5_Cy5", "G5_Cy5.5",   "I14_Cy5", "I14_Cy5.5", "I14_ROX", "I15_ROX","I18_JOE", "I18_TAMRA", "I2_FAM", "I2_JOE", "I2_ROX", "I2_TAMRA", "I3_Cy5", "I3_Cy5.5", "I4_Cy5", "I4_Cy5.5", "I5_Cy5", "I5_Cy5.5", "I5_ROX", "I6_ROX", "I7_FAM", "I8_FAM", "I9_JOE", "I9_TAMRA", "K12_Cy5", "K12_Cy5.5", "K13_Cy5", "K13_Cy5.5", "K18_JOE", "K18_TAMRA", "K2_FAM", "K2_JOE", "K2_ROX", "K2_TAMRA", "K3_Cy5", "K3_Cy5.5", "K4_Cy5", "K4_Cy5.5", "K5_Cy5", "K5_Cy5.5", "K5_ROX", "K6_ROX", "K7_FAM", "K8_FAM", "M14_Cy5", "M14_Cy5.5", "M14_ROX", "M15_ROX", "M16_FAM", "M17_FAM", "M2_FAM", "M2_JOE", "M2_ROX", "M2_TAMRA", "M3_Cy5", "M3_Cy5.5", "M4_Cy5", "M4_Cy5.5", "M5_Cy5", "M5_Cy5.5", "M5_ROX", "M6_ROX", "M7_FAM", "M8_FAM", "M9_JOE", "M9_TAMRA","O11_ROX","O14_Cy5.5",   "O15_ROX", "O16_FAM",  "O18_JOE", "O18_TAMRA", "O2_FAM", "O2_JOE", "O2_ROX", "O2_TAMRA", "O3_Cy5", "O3_Cy5.5", "O4_Cy5", "O4_Cy5.5", "O5_Cy5", "O5_Cy5.5", "O5_ROX", "O6_ROX", "O7_FAM", "O8_FAM", "O9_JOE", "O9_TAMRA", "G8_FAM", "A14_ROX")

Exp1142_nsp2_canon <- Exp1142 |> 
  filter(!variable %in% c(noncanon, drop)) |> 
  mutate(subset = "canon")

test_plot_save(Exp1142_nsp2_canon)

Exp1142_nsp2_noncanon <- Exp1142 |> 
  filter(variable %in% c(noncanon)) |> 
  mutate(subset = "noncanon")

test_plot_save(Exp1142_nsp2_noncanon)

 
tally_dsfbase()
# 73 proteins and 1080 datasets in SYPRO cannon,
# 69 proteins and 1469 in cannon (not SYPRO),
# 114 proteins and 1618 datasets in non-cannon
```

```{r}
Exp1120 <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp1120--20210409_nsp3_mac1_mergers_and_leadlikes_T004/int/Exp1120--20210409_cleaned_data.rds")[[2]] |> 
  filter(protein == "SP150_Nsp3",
         channel_f == "FAM") |> 
  select(-c(channel,
         volume,
         ID,
         Barcode,
         DMSO_stock_conc,
         PO,
         soaking_tested,
         plate_number)) |> 
  mutate(id = "placeholder",
         subset = "canon",
         type = "protein")

# initially define non-canon as the curves whch have high initial RFU
## noncanon
Exp1120_nsp3mac1_noncanon <- Exp1120 |> 
  filter(column != 24) |> 
  group_by(variable) |> 
  mutate(subset = case_when(any(Temperature < 45 & value_norm > 0.14) ~ "noncanon")) |> 
  ungroup(variable) |> 
  filter(subset == "noncanon")

 Exp1120_nsp3mac1_noncanon |> test_plot_save()

## canon
Exp1120_nsp3mac1_canon <- Exp1120 |> 
  filter(column != 24,
         well != "A23") |> # gross drop
  group_by(variable) |> 
  mutate(subset = case_when(any(Temperature < 45 & value_norm > 0.15) ~ "noncanon", .default = "canon")) |> 
  ungroup(variable) |> 
  filter(subset == "canon")

Exp1120_nsp3mac1_canon |> test_plot_save()

# Exp1120_nsp3mac1_canon$variable |> n_distinct()
# [1] 2133

## gotchas
 Exp1120_nsp3mac1_gotcha <- Exp1120 |> 
  filter(column == 24 | well == "A23") |> # instrument read issue
  mutate(subset = "gotcha")

  Exp1120_nsp3mac1_gotcha |> test_plot_save()
```


Source 2: PLPro, ISG15, and diUB
- Exp1201_PLPro_ISG15_Ub_canon
- Exp1201_PLPro_ISG15_Ub_noncanon
```{r}
Exp1201_PLPro_ISG15_Ub <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp1201--20210801_PLPro_ISG15_Ub_DRC/intermediates/Exp1201--20210801_df_all.rds") |> 
  filter(prot_combo != "Empty",
         channel_f %in% c("ROX", "Cy5", "Cy5.5")) |> 
    group_by(variable) |> 
  filter(any(value > 5000)) |>  # these are noncanon
  ungroup() |> 
  mutate(id = "placeholder")


Exp1201_PLPro_ISG15_Ub_canon <- Exp1201_PLPro_ISG15_Ub |> 
  filter(row != "I") |> 
  mutate(subset = "canon") 

Exp1201_PLPro_ISG15_Ub_canon |> test_plot_save()

Exp1201_PLPro_ISG15_Ub_noncanon <- Exp1201_PLPro_ISG15_Ub |> 
  filter(row == "I") |> 
  mutate(subset = "noncanon") 

Exp1201_PLPro_ISG15_Ub_noncanon |> test_plot_save()
```

```{r}
tally_dsfbase()
# 73 proteins and 1080 datasets in SYPRO cannon,
# 70 proteins and 3602 in cannon (not SYPRO),
# 115 proteins and 1692 datasets in non-cannon

# nsp3mac1 screen has 2133 canon

# 3696 - 2133 # 1563
# 73 proteins and 1080 datasets in SYPRO cannon,
# 73 proteins and 3696 in cannon (not SYPRO),
# 116 proteins and 1698 datasets in non-cannon

## Goal:
# 1000 SYPRO canon <- get rid of80
# 1500 non sypro canon <- get rid of 63
# 1500 non canon <- get rid of ~80
# the mac1 dataset 
# the gotchas
```

```{r}
Exp1120_nsp3mac1_gotcha <- Exp1120 |> 
  filter(column == 24) |> 
  mutate(subset = "gotcha")

Exp1120_nsp3mac1_gotcha |> test_plot_save() 

Exp1120_nsp3mac1_canon <- Exp1120 |> 
  filter(column != 24) |> 
  mutate(subset = "canon")

 Exp1120_nsp3mac1_canon |> test_plot_save() 
  
noncanon <- c("A1_FAM_p1", "A1_FAM_p1_low", "A1_FAM_p2", "A1_FAM_p2_low", "A1_FAM_p3", "A1_FAM_p3_low","A10_FAM_p2_low","A13_FAM_p1","A19_FAM_p1", "B1_FAM_p1", "B1_FAM_p2", "B1_FAM_p3", "B13_FAM_p1", "B19_FAM_p1", "C1_FAM_p1", "C1_FAM_p2", "C1_FAM_p3", "C13_FAM_p1", "C19_FAM_p1", )

gotcha <- c("A22_FAM_p1", "A22_FAM_p1_low", "A22_FAM_p2", "A22_FAM_p2_low", "A22_FAM_p3", "A22_FAM_p3_low", "A23_FAM_p1", "A23_FAM_p1_low", "A23_FAM_p2", "A23_FAM_p2_low", "A23_FAM_p3", "A23_FAM_p3_low", "A24_FAM_p1", "A24_FAM_p1_low", "A24_FAM_p2", "A24_FAM_p2_low", "A24_FAM_p3", "A24_FAM_p3_low", "A5_FAM_p3", "B1_FAM_p1_low", "B1_FAM_p2_low", "B1_FAM_p3_low", "B24_FAM_p1", "B24_FAM_p1_low", "B24_FAM_p2", "B24_FAM_p2_low", "B24_FAM_p3", "B24_FAM_p3_low")



print_quote(Exp1120$variable)
```



Source: nsp3 with multiple dyes, DRC
```{r}
# you have to maybe get/find the raw data from this directory
"/Users/taiaseanwu/Box Sync/data/Exp1192--20210713_nsp3_compound_sensitivity_by_dye_repeat"
```



```{r}
# option -- some MWF08 data
# "/Users/taiaseanwu/Box Sync/data/Exp1051--20210105_FPN_meeting_1/data/Exps_to_date/Exp1021--20201218_SP203_FPN_MWF08_hepcidin/processed_screen/Exp1021_2020-12-19_df_all.rds"

# option -- some validation data with nanodiscs
# "/Users/taiaseanwu/Box Sync/data/Exp1129--20210422_FPN_detective_work_when_did_stuff_stop_working/data/Exp1022--20201219_SP203_SP204_FPN_LMNG_nanodisc_validation/processed_screen/Exp1022_FPN_2020-12-20_df_all.rds"

# option -- up down screen
# "/Users/taiaseanwu/Box Sync/data/Exp1051--20210105_FPN_meeting_1/data/Exps_to_date/Exp1025--20201219_SP204_FPN_nanodisc_up_down_dye_screen_1023/processed_screen/Exp1025_2020-12-20_df_all.rds"

# potential best option -- from shape classes. but this might be over-processed...?
# "/Users/taiaseanwu/Box Sync/data/Exp1129--20210422_FPN_detective_work_when_did_stuff_stop_working/data/Exp1042--20201230_FPN_nanodisc_shape_class_next_step_planning/raw/Exp1025_2020-12-20_df_all.rds"

## other good option -- up down validation
# "/Users/taiaseanwu/Box Sync/data/Exp1254--20211208_figure3c_FPN_and_nuc_highlights/input_data/FPN/with_best_dyes/Exps_to_date/Exp1049--20210102_FPN_ND_up_down_validation/analyzed_screens/Exp1049_2021-01-03_df_all.rds"
# "/Users/taiaseanwu/Box Sync/data/Exp1254--20211208_figure3c_FPN_and_nuc_highlights/input_data/FPN/with_best_dyes/Exps_to_date/Exp1049--20210102_FPN_ND_up_down_validation/analyzed_screens/Exp1049_2021-01-03_manually_called_hits.csv"

## up down wit hcompoujnds -- see notebook for definiton of best dyes
# "/Users/taiaseanwu/Box Sync/data/Exp1254--20211208_figure3c_FPN_and_nuc_highlights/input_data/FPN/with_best_dyes/Exp1059--20210118_FPN_up_down_with_compounds/raw/Exp1059_2021-01-21_df_all.rds"


## with compounds, only maybe worth putting in
# "/Users/taiaseanwu/Box Sync/data/Exp1129--20210422_FPN_detective_work_when_did_stuff_stop_working/data/Exp1084--20210212_FPN_ND_with_compounds_repeat_no_incubation/raw/Exp1084_FPN_with_compounds_2021-02-25_df_all.rds"


## wit hcompounds -- worth looking at again
# "/Users/taiaseanwu/Box Sync/data/Exp1084--20210212_FPN_ND_with_compounds_repeat_no_incubation/raw/Exp1084_FPN_with_compounds_2021-02-25_df_all_reformatted.rds"


```
#######

Source: nsp3 with multiple dyes, DRC
```{r}
# you have to maybe get/find the raw data from this directory
"/Users/taiaseanwu/Box Sync/data/Exp1192--20210713_nsp3_compound_sensitivity_by_dye_repeat"
```




```{r}
# # more good PLPro data
# "/Users/taiaseanwu/Box Sync/data/Exp0983--20201202_PLPro_GRL0617_with_dyes/analyzed/SP198_PLPro_2020-12-03_df_all.rds"
```


