---
title: "R Notebook"
output: html_notebook
---

Read in the tidied DSFbase curves and add IDs
Plot, and edit assignments

```{r}
library(tidyverse)
library(fs)
library(testthat)
library(glue)
source("R/collect_dsf_data.R")
```

# Number of proteins
# Number of different experimental conditions
# Types or experiments

Read combined dsfbase files
```{r}
id_map <- read_rds("../03_combined_data/dsfbase_id_map.rds")
dsfbase <- read_rds("../03_combined_data/dsfbase.rds")
```

High-level descriptors
```{r}
# number of proteins in the dataset: 107
n_proteins <- dsfbase$protein |> n_distinct() # [1] 107

# number of different experiments: 83
n_exp <- dsfbase |> 
  mutate(exp_num = 
  gsub(directory, pattern = "../02_aggregated_data/canon/|../02_aggregated_data/noncanon/|../02_aggregated_data/SYPRO_canon/|../02_aggregated_data/SYPRO_noncanon/|../02_aggregated_data/gotcha/",
        replacement = "") ) |> 
  separate(exp_num, c("exp_num"), sep = "_", extra = "drop") |> 
  pull(exp_num) |> 
  n_distinct()

# n_exp # [1] 83

# date range of experiments: December 2018 to December 2021
exp_sorted <- sort(unique(dsfbase$directory))
## printed and looked manually for the range of experiment numbers. Looked up dates in notebook.
# first experiment: "../02_aggregated_data/canon/Exp0469_eIF2B_with_ISRIB_canon.rds" -- 2018-12-05 
# last experiment: "Exp1256_SP215_caspase1_zymogen_gotcha.rds"  -- 2021-12-10
first_date <- "December 2, 2018" 
last_date <- "December 10, 2021"

# Instruments: five different qTowers, plus one other BioRad CFX
n_qtower <- 4
n_biorad <- 1
n_instruments <- n_qtower+n_biorad

# n datasets
n_datasets <- n_distinct(dsfbase$id)

msg_datasets <- glue("{n_datasets} unique DSF datasets, each containing 69 temperature measurements")
msg_protein <- glue("{n_proteins} different proteins, spanning")
msg_exp <- glue("{n_exp} different experiments")
msg_dates <- glue("performed at the Mission Bay Campus of the University of California San Francisco 
                  between {first_date} and {last_date}, using")
msg_instruments <- glue("{n_instruments} different intruments ({n_qtower} Analytik Jena qTower 384Gs, and {n_biorad} BioRad CFX")
msg_total <- glue("DSFbase contains:\n. {msg_datasets}\n. {msg_protein} \n. {msg_exp} \n. {msg_dates} \n. {msg_instruments}")
print(msg_total)

"Each dataset contains: "
n_temps <- n_distinct(dsfbase$Temperature)
min_temp <- min(dsfbase$Temperature)
max_temp <- max(dsfbase$Temperature)
diff_temp <- 1

glue("Each dataset contains RFU measurements taken {max_temp - min_temp}  RFU measurements made across temperatures, from {min_temp}  to {max_temp} ºC, with temperature increments of {diff_temp} ºC per measurment.")

```
Subset descriptors
```{r}
dsfbase |> 
  select(subset, id) |> 
  distinct() |> 
  group_by(subset) |> 
  tally()
```


Plot all of each subset
```{r}
plot_subset <- function(dsfbase, 
                        .subset, 
                        save_path = "../03_combined_data/plots",
                        .test_subset = TRUE,
                        .facet_by = "short_id"){
  

  
  dsf <- dsfbase |> 
    mutate(short_id = str_sub(id, start = -8, end = -1)) |> 
    filter(subset == .subset) |> 
    group_by(id) |> 
    mutate(value_norm = scales::rescale(value, c(0,1))) 

    
  if(.test_subset) { # take only the first 20
    dsf <- dsf |> 
      filter(id %in% unique(dsf$id)[c(1:20)])
  }
  
    plot_title <- glue("DSFbase, all datasets in `{.subset}` subset")
    n_prot <- n_distinct(dsf$protein)
    n_ids <- n_distinct(dsf$id)
  plot_subtitle <- glue("{n_ids} datasets from {n_prot} proteins")
    
   p <- dsf |>  ggplot(aes(x = Temperature, y = value_norm)) +
    geom_line(linewidth = 0.3) +
    facet_wrap(~.data[[.facet_by]], scales = "free", ncol = 20) +
    hrbrthemes::theme_ipsum(base_family = "Helvetica",
                            base_size = 5,
                            strip_text_size = 8) +
       hrbrthemes::theme_ipsum(base_family = "Helvetica") +
      theme(aspect.ratio = 1,
          axis.text.y=element_blank(),
          axis.text.x=element_blank(),
          panel.spacing = unit(.2, "lines"),
          strip.text = element_text(size = 5, margin = margin(0.2,0,0,0, "cm"))) +
  facet_wrap(~short_id, ncol = 10) +
     labs(title = plot_title,
          subtitle = plot_subtitle,
          y = "Normalized RFU",
          x = "Temperature (ºC)")
  
    ## get save name
  save_name <- glue::glue("{save_path}/{.subset}.pdf")
  save_height <- (7/10)*(n_distinct(dsf$id)/10) + 3
  
  ggsave(save_name,
         p,
         width = 7,
         height = save_height,
         limitsize = FALSE
  )
  
  p
}

p_test <- plot_subset(dsfbase, "SYPRO_canon", .test_subset = FALSE)
```

Figure out which elements to drop
```{r}
p_SYPR0_canon <- plot_subset(dsfbase, "SYPRO_canon", .test_subset = FALSE)

# want to drop 80
# 73 proteins and 1080 datasets in SYPRO cannon,
tally_dsfbase()

c("ID000007","ID000006", "ID000524":"ID000526","ID000543", "ID000544",
  "ID000565",
  "ID001055", "ID001062", "ID001063","ID001064", )
drop <- ("ID000437")

1080+3696
```

```{r}
p_canon <- plot_subset(dsfbase, "canon", .test_subset = FALSE)
```

```{r}
p_noncanon <- plot_subset(dsfbase, "noncanon", .test_subset = FALSE)
```

```{r}
p_edit <- p_test + 
  hrbrthemes::theme_ipsum(base_family = "Helvetica") +
      theme(aspect.ratio = 1,
          axis.text.y=element_blank(),
          axis.text.x=element_blank(),
          panel.spacing = unit(.2, "lines"),
          strip.text = element_text(size = 5, margin = margin(0.2,0,0,0, "cm"))) +
  facet_wrap(~short_id, ncol = 10)

  ggsave("../03_combined_data/plots/gotcha.pdf", p_edit, height = 20, width = 7)

dsfbase |> head()
substr("DSFbase001_SYPRO_canon_ID000001", start = 1, stop = -10)
str_sub()
str_sub("DSFbase001_SYPRO_canon_ID000001", start = -8, end = -1)
```



Create a description file for the different experiments
```{r}
seek_tally <- 
  function(DATASET_DIR, tally_col = "variable"){
    dsf <- read_rds(DATASET_DIR) 
    n <- n_distinct(dsf[[tally_col]])
}


summarise_datasets <- 
  function(DSFBASE_DIR,
           subset_levels = c("SYPRO_canon", "canon", "SYPRO_noncanon", "noncanon", "gotcha"),
                                                 ...){
    
  all_dirs <- fs::dir_ls(DSFBASE_DIR, recurse = 1, regexp = ".rds")
 
  variable_tallies <- sapply(all_dirs,
                           seek_tally)
  
  all_file_names <-  all_dirs |> 
  tibble(directory = _) |> 
  mutate(X1 = gsub(directory, pattern = "../02_aggregated_data/", replacement = "")) |> 
  separate(X1, into = c("subset_f", "file_name"), sep = "/") |> 
  mutate(subset_f = factor(subset_f, levels = subset_levels)) |> 
  relocate(subset_f) |> 
  arrange(subset_f) |> 
    separate(file_name, c("exp_num", "protein"), extra = "merge") 
  
  # these we should do on the full dataset, since some of these files contain more than one protein
  # |> 
  # mutate(n_datasets = variable_tallies) |> 
  # separate(file_name, c("exp_num", "protein"), extra = "merge") |> 
  # mutate(protein = gsub(protein, pattern = "_SYPRO_canon.rds|_SYPRO_noncanon.rds|_canon.rds|_noncanon.rds|_gotcha.rds",
  #                       replacement = ""))
}
```

Read in the dye master spreadsheet for labeling
```{r}
dye_master <- 
  readxl::read_excel("/Users/taiaseanwu/Box Sync/data/Exp1442--20230720_dye_screen_raw_data_tidy/0_input/Exp1304--20220412_dye_screen_master_spreadsheet.xlsx") |> 
  separate(screen_name, c("exp_num", "protein"), 
           sep = "--|_", 
           extra = "merge") |> 
  select(exp_num, protein_conc_uM:experimental_notes) |> 
  distinct() |> 
  mutate(instrument = "AnalytikJena_qTower384G")

dye_master |> filter(exp_num != "Exp0947")

dye_master$exp_num |> table()
```

Read in and add dye screen annotations
```{r}
dsfbase_names <- 
  summarise_datasets("../02_aggregated_data") 

dsfbase_summary <- dsfbase_names |> 
  left_join(x = _, y = dye_master |> filter(exp_num != "Exp0947"), by = "exp_num")
```

