---
title: "R Notebook"
output: html_notebook
---

Combine the entries from the dye screens and non-dye screen experiments. 

These entries all have preliminary assignments, which will be revised in the next notebook.
The IDs added here are to support the revision of assignments, and are not the final IDs

```{r}
library(testthat)
library(glue)
library(tidyverse)
source("R/functions/utils.R")
source("R/functions/add_IDs.R") # function to add new IDs
source("R/functions/facet_plot_entries.R") # function to add new IDs
source("R/functions/save_dsfbase.R") # function to save standard dsfbase output files
```

Read in the annotated experiments
```{r}
annotated <- bind_rows(read_rds("../01_annotated_entries/dye_screens/all_dye_screens_annotated.rds"), # dye screens
                        read_rds("../01_annotated_entries/non_dye_screens/all_non_dye_screens_annotated.rds")) |>  # non dye screens
  
  # add the subsubsets, which will be amended in the next notebook
  mutate(subsubset = subset,
         subsubset_f = factor(subsubset, levels = c("SYPROcanon", "canon", "SYPROmidcanon", "midcanon", "SYPROnoncanon", "noncanon", "SYPROlatenoncanon", "latenoncanon", "errata")))

annotated$variable |> n_distinct() # [1] 6239

test_annotated_dataset(annotated)
```

Directories to save the outputs
```{r}
save_preliminary_to <- "/Users/taiaseanwu/Desktop/programming/dsfbase/20231205_version/02_combined_dsfbase/01_preliminary_subsets/data/"
save_preliminary_plots_to <- "/Users/taiaseanwu/Desktop/programming/dsfbase/20231205_version/02_combined_dsfbase/01_preliminary_subsets/plots/"

# create directories if they do not already exist
fs::dir_create(save_preliminary_to)
fs::dir_create(save_preliminary_plots_to)
```

Add IDs
```{r}
dsfbase_preliminary <- add_IDs(annotated)
```

Save the preliminary version of DSFbase, for record keeping
```{r}
# data
write_rds(dsfbase_preliminary, glue::glue("{save_preliminary_to}dsfbase_annotated.rds"))

# plots
all_subsets <- c("errata", "SYPROcanon", "canon", "SYPROnoncanon", "noncanon")
lapply(all_subsets, plot_subset, dsfbase = dsfbase_preliminary, save_path = save_preliminary_plots_to, .test_subset = FALSE)
```

Save this tibble also into the assignment amendment folder to be read and used in the next notebook
```{r}
write_rds(dsfbase_preliminary, "/Users/taiaseanwu/Desktop/programming/dsfbase/20231205_version/02_combined_dsfbase/02_subset_amendments/to_reassign/dsfbase_to_update.rds")
```





