---
title: "R Notebook"
output: html_notebook
---

```{r}
library(testthat)
library(tidyverse)
source("R/functions/tests.R")
```

Read in the annotated non dye screen experiments
```{r}
### `annotated_non_dye_screen.rds`created in notebook: YY_annotate_entries.Rmd
# that notebook is messy and needs cleaning, but right now, just use the final object. 

ANNOTATION_DIR <- "../00_inputs/additional_experiments/annotated_additional_experiments/annotated_non_dye_screen.rds"

annotated_experiments <- read_rds(ANNOTATION_DIR) |> 

  # column unfilled in this tibble -- is NA for all  
  select(-directory) |> 
  
  # these are pre human-readable protein names
  # which matches contents of column 'protein_original' in the raw data
  rename(protein_original = protein) |> 
  
  # this is more completely contained in the raw data
  select(-subset)
```

Read in the raw data, aggregated for all experiments (including dye screens).
```{r}
RAW_DIR <- "/Users/taiaseanwu/Desktop/programming/dsfbase/03_combined_data/dsfbase.rds"

dsfbase_raw_experiments <- read_rds(RAW_DIR) |> 
  
  # add an exp_num column, to join with the annotations
  mutate(exp_num = gsub(pattern = "../02_aggregated_data/SYPRO_canon/|../02_aggregated_data/SYPRO_noncanon/|../02_aggregated_data/canon/|../02_aggregated_data/noncanon/|../02_aggregated_data/errata/|../02_aggregated_data/gotcha/|.rds",
                        replacement = "",
                        directory)) |> 
  separate(exp_num, into = c("exp_num", "exp_name"), sep = "_", extra = "merge") |> 
  select(-exp_name) |> 
  
  # add a variable column (but this needs annotations still to be completely unique)
  # because we need the thermocycling conditions
  #unite(variable, c(exp_num, variable, protein_original), sep = "__", remove = FALSE) |> 
  
  # keep only the non dye screens
  filter(exp_num %in% annotated_experiments$exp_num)

## test_dataset(dsfbase_raw)
# doesn't yet pass -- variable is not unique
# adding thermocycling protocol in the next step will likely resolve this
```

```{r}
exp1120_only <- read_rds("/Users/taiaseanwu/Desktop/programming/dsfbase/20231205_version/00_inputs/additional_experiments/annotated_additional_experiments/Exp1120_annotated.rds")
                         
                         dsfbase_raw_experiments |> filter(exp_num == "Exp1120",
                                                           is.na(Temperature)) 
```


Check that the experiments are the same in all
```{r}
# ensure we have all expected experiments in both 
all(dsfbase_raw_experiments$exp_num %in% annotated_experiments$exp_num) # [1] TRUE
all(annotated_experiments$exp_num %in% dsfbase_raw_experiments$exp_num) # [1] TRUE

# the protein column in the annotated experiments is the same as the protein_original column
all(annotated_experiments$protein_original %in% dsfbase_raw_experiments$protein_original) # [1] TRUE
all(dsfbase_raw_experiments$protein_original %in% annotated_experiments$protein_original) # [1] TRUE
```

Combine annotations and raw data
```{r}
annotated_dsfbase_experiments <- 
  dsfbase_raw_experiments |> 
  left_join(annotated_experiments, by = join_by(id, protein_original, well, variable, exp_num)) |> #, protein, subset, well, variable, directory))
  unite(variable, c(exp_num, variable, protein_original, thermocycling_protocol), sep = "__", remove = FALSE) |> 
  
  # these two experimenbts have issues with annotation, and it's not worth the hours it's taking to figure that out
  filter(!is.na(thermocycling_protocol) & !exp_num %in% c("Exp1033")) #, "Exp1120"))

test_annotated_dataset(annotated_dsfbase_experiments, .id_col = "id") # all pass
test_annotated_dataset(annotated_dsfbase_experiments, .id_col = "variable") # all pass, after `filter(!is.na(thermocycling_protocol) & exp_num %in% c("Exp1033"))

 n_distinct(annotated_dsfbase_experiments$variable) # [1] 5341 (seems about right)
```

Save annotated experiments
```{r}
write_rds(annotated_dsfbase_experiments, "/Users/taiaseanwu/Desktop/programming/dsfbase/20231205_version/01_annotated_entries/non_dye_screens/all_non_dye_screens_annotated.rds")
```











#### scratch work, to try to hunt down which entries aren't uniquely identified by variables and ids
## in the end, decided to get rid of the problematic entries for Exp1033 and Exp1120, because it was too annoying and slow to figuero ut
##  and these entires were not particularly important anyway. 
There are about 200 IDs in raw DSFbase that are not in the annotated entries. 
Are these the duplicate assignments? If so, we can just drop them... 
```{r}
missing_ids <- unique(dsfbase_raw_experiments$id[!dsfbase_raw_experiments$id %in% annotated_experiments$id])
missing_ids

dsfbase_missing_id_vars <- 
  dsfbase_raw_experiments |> 
  filter(id %in% missing_ids) |> 
  select(id, variable) |> 
  distinct() |> 
  arrange(variable) |> 
  pull(variable)

dsfbase_raw_experiments |> 
  filter(variable %in% dsfbase_missing_id_vars) |> 
  select(id, variable, exp_num) |> distinct() |> group_by(variable) |> tally() |> arrange(desc(n))

#### test the raw data going in
test_experiment <- function(dsf, .exp_num){
  print(.exp_num)
  
  test_exp <- dsf |> 
  filter(exp_num == .exp_num) |> 
  select(all_of(c("id", "subset", "protein", "well", "variable", "Temperature", "value"))) |> 
    mutate(subset = as.character(subset),
           id = as.character(id))

try(test_dataset(test_exp))
}

missing_id_exps <- dsfbase_raw_experiments |> 
  filter(variable %in% dsfbase_missing_id_vars) |> 
  pull(exp_num) |> 
  unique()

lapply(missing_id_exps, test_experiment, dsf = dsfbase_raw_experiments)


###### test the annotated
test_annotated_dataset_filter <- function(dsf, .exp_num){
  print(.exp_num)
  
  test_exp <- dsf |> 
  filter(exp_num == .exp_num)

try(test_annotated_dataset(test_exp))
  
}

lapply(unique(annotated_dsfbase$exp_num), test_annotated_dataset_filter, dsf = annotated_dsfbase)

### 

annotated_dsfbase |> filter(exp_num == "Exp1033") 
  group_by(variable) 

# ids are unique, but variables are not 
test_annotated_dataset(annotated_dsfbase |> filter(exp_num == "Exp1033"), .id_col = "id")


dup_var_1033 <- annotated_dsfbase |> filter(exp_num == "Exp1033") |> select(id, variable) |> group_by(variable) |> tally() |> filter(n>1) |> pull(variable)

annotated_dsfbase  |> 
  filter(exp_num == "Exp1033",
         variable %in% dup_var_1033) |> 
  ggplot(aes(x = Temperature, y = value, group = variable)) +
  geom_line() +
  facet_wrap(~thermocycling_protocol)


annotated_dsfbase |> filter(is.na(thermocycling_protocol))  |> pull(exp_num) |> table()
```


```{r}
test_experiment(dsfbase_raw_experiments, "Exp0849")

# these ones don't pass dataset tests
# [1] "Exp1120" <- has duplicated assignments
# [1] "Exp1033" <- actually has an issue with the variable column

dup_var_1033 <- dsfbase_raw_experiments |> 
  filter(exp_num == "Exp1033") |> 
  group_by(variable) |> 
  tally() |> 
  arrange(desc(n)) |> 
  filter(n != 70) |> 
  pull(variable)

dsfbase_raw_experiments |> 
  filter(exp_num == "Exp1033") |> 
  filter(variable %in% dup_var_1033) |> 
  ggplot(aes(x = Temperature, y = value, group = variable)) +
  geom_line()

dup_var_1120 <- dsfbase_raw_experiments |> 
 
  filter(exp_num == "Exp1120") |> 
  select(-c(id, subset, directory)) |>  
  distinct() |> 
  group_by(variable) |> 
  tally() |> 
  arrange(desc(n)) |> 
  filter(n != 70) |> 
  pull(variable)


# this one is actual duplicated datasets assignments
dsfbase_raw_experiments |> 
  filter(exp_num == "Exp1120") |> 
  
  filter(variable %in% dup_var_1120) #|> 
  ggplot(aes(x = Temperature, y = value, group = variable)) +
  geom_line()
```



```{r}
## check -- some curves have two IDs, because I accidentally assigned them to two different subset
# (note that in the updated dye screen processing, this isn't possible, but for these screens,
# which i made with the earlier, worse functions, it is)

dup_vars <- annotated_dsfbase |> 
  select(id:subset, well, directory, exp_num:additional_notes) |> 
  distinct() |> 
  group_by(variable) |> 
  tally() |> 
  filter(n!=1) |> 
  pull(variable)

dup_vars

annotated_dsfbase |> 
  filter(variable %in% dup_vars) |> 
  ggplot(aes(x = Temperature, y = value_norm, group = variable)) +
  geom_line() +
  facet_wrap(~variable)


annotated_dsfbase |> 
  select(-c(id, subset, directory)) |> 
  distinct() |> 
  nrow() # [1] 391790

annotated_dsfbase

annotated_dsfbase |> 
  distinct() |> 
  nrow() # [1] 392140


annotated_dsfbase |>  
  group_by(id, subset, directory) |> 
  tally() |> 
  filter(n != 70)

annotated_dsfbase |> 
  filter(variable %in% dup_vars)
```


```{r}
test_annotated_dataset(annotated_dsfbase, .id_col = "id")

annotated_dsfbase |> group_by(variable) |> select(variable, id) |> tally() |> arrange(n)



dsfbase_raw
annotated_experiments

annotated_dsfbase$exp_num |> table()

experimental_conditions <- annotated_dsfbase |> select(-c(Temperature, value, value_norm)) |> distinct()

test_experimental_conditions(experimental_conditions, .id_col = "id")
experimental_conditions
```

```{r}
test_experimental_conditions <- function(annotated, 
                            .use_template = FALSE, 
                            .external_template = NULL,
                            .id_col = "variable") {
  
  if(.use_template) {
    template <- .external_template
  } else {
    template <- tibble("id" = character(),
                       "well" = character(),
                       "exp_num" = character(),
                       "exp_summary" = character(),
                       "variable" = character(),
                       "protein" = character(),
                       "protein_concentration_uM" = numeric(),
                       
                       "dye" = character(),
                       "dye_concentration_uM" = numeric(),
                       "buffer" = character(),
                       "additive" = character(),
                       "additive_description" = character(),
                       "additive_concentration_uM" = numeric(),
                       "thermocycling_protocol" = character(),
                       "fluorescent_channel" = character(),
                       "instrument" = character(),
                       "additional_notes" = character(),
                       "directory" = character(),
                       "subset" = character())
  }
  
  # ----- Column names
  test_that("annotations includes reqiured columns", {
    expect_in(names(template), names(annotated))
  })
  
  # test_that("data has 'variable' column which is genuinely unique to a single trace", {
  #   temp_dup <- annotated %>%
  #     dplyr::group_by(.data[[.id_col]]) %>%
  #     dplyr::mutate(unique_temps = !duplicated(Temperature))
  #   
  #   expect_true(all(temp_dup$unique_temps))
  # })
  

  # dataset value contains one of the accepted names
  test_that("dataset contains one of the accepted values", {
    subset_names <- c(
      "SYPROcanon",
      "SYPROnoncanon",
      "canon",
      "noncanon",
      "errata",
      "buffer"
    )
    expect_in(annotated$subset, subset_names)
  })
  
  # test for post-assignments
  test_that("all variables have a single assignment", {
    int <- annotated |> 
      select(all_of(c(.id_col, "subset"))) |> 
      distinct() |> 
      group_by(.data[[.id_col]]) |> 
      tally()
    expect_true(all(int$n == 1)) })
  
  # ---- no duplicate ID annotations
  test_that("Only one annotation per ID", {
    expect_true(n_distinct(annotated$id) == length(annotated$id))
  })
  
}

```

Simplify to just the 
```{r}

```

Determine the number of entries
```{r}
annotated_dsfbase$id |> n_distinct() # [1] 6686 <- pretty much the right number. Great! 
```


Automated tests
```{r}

```


```{r}
test_annotated <- function(){
  
}


mtgroup <- "cyl"

mtcars |> group_by(.data[[mtgroup]]) |> summarise()
mtcars |> group_by(cyl) |> summarise()
```



```{r}
test_annotation(annotated_experiments)
```


