---
title: "R Notebook"
output: html_notebook
---

Combine the entries from the dye screens and non-dye screen experiments. 

These entries all have preliminary assignments, which will be revised in the next notebook.
The IDs added here are to support the revision of assignments, and are not the final IDs

```{r}
library(testthat)
library(glue)
library(tidyverse)
source("R/functions/utils.R")
source("R/functions/add_IDs.R") # function to add new IDs
source("R/functions/facet_plot_entries.R") # function to add new IDs
source("R/functions/save_dsfbase.R") # function to save standard dsfbase output files
```

<!-- Read in the annotated experiments -->
<!-- ```{r} -->
<!-- annotated <- bind_rows(read_rds("../01_annotated_entries/dye_screens/all_dye_screens_annotated.rds"), # dye screens -->
<!--                         read_rds("../01_annotated_entries/non_dye_screens/all_non_dye_screens_annotated.rds")) |>  # non dye screens -->

<!--   # add the subsubsets, which will be amended in the next notebook -->
<!--   mutate(subsubset = subset, -->
<!--          subsubset_f = factor(subsubset, levels = c("SYPROcanon", "canon", "SYPROmidcanon", "midcanon", "SYPROnoncanon", "noncanon", "SYPROlatenoncanon", "latenoncanon", "errata"))) -->

<!-- annotated$variable |> n_distinct() # [1] 6239 -->

<!-- test_annotated_dataset(annotated) -->
<!-- ``` -->

<!-- Create a folder to manually edit protein names and re-join with data -->
<!-- ```{r} -->
<!-- protein_name_map <-  -->
<!--   annotated %>%  -->
<!--   select(protein, protein_original, exp_num, additional_notes, exp_summary) %>%   -->
<!--   distinct()  -->


<!-- annotated  %>% select(protein, protein_original, exp_num, additional_notes, exp_summary) %>%   -->
<!--   distinct()  -->

<!-- protein_name_map %>% write_csv("../01_annotated_entries/protein_names/original_protein_names.csv") -->

<!-- protein_names_updated <- read_csv("../01_annotated_entries/protein_names/updated_protein_names_v2.csv") -->

<!-- # check that protein names  -->
<!-- protein_names_updated %>%  -->
<!--   select(protein_name_short, protein_name_long) %>%  -->
<!--   distinct() %>%  -->
<!--   group_by(protein_name_short) %>%  -->
<!--   tally() %>%  -->
<!--   filter(n != 1) -->
<!-- # 0 rows -->

<!-- protein_names_updated %>%  -->
<!--   select(protein_name_short, protein_name_long) %>%  -->
<!--   distinct() %>%  -->
<!--   group_by(protein_name_long) %>%  -->
<!--   tally() %>%  -->
<!--   filter(n != 1) -->
<!-- # 0 rows -->

<!-- nonunique <- protein_names_updated %>%  -->
<!--   distinct() %>%  -->
<!--   # select(protein_name_short, protein_name_long) %>%  -->
<!--   # distinct() %>%  -->
<!--    group_by(protein, protein_original, exp_num, exp_summary, additional_notes) %>%  -->
<!--   tally() %>%  -->
<!--   filter(n != 1) -->
<!--   pivot_wider(id_cols = c("protein", "protein_original", 'exp_num', "exp_summary", "additional_notes")) -->

<!-- nonunique -->
<!-- ``` -->
<!-- Update protein names -- and save to amend the final DSFbase annotations -->
<!-- ```{r} -->
<!-- annotated_renamed <-  -->
<!--   annotated %>%  -->
<!--   left_join(protein_names_updated, -->
<!--               by = join_by(protein,  -->
<!--                            protein_original,  -->
<!--                            exp_num,  -->
<!--                            exp_summary,  -->
<!--                            additional_notes)) %>%  -->
<!--   select(-c("id_num", # unnecessary helper column from the names update list -->
<!--             "protein", # updated/improved by "protein_name_long" -->
<!--             "protein_original" # updated/improved by "protein_name_short" -->
<!--             )) %>%  -->
<!--   # rename(protein = protein_name_long, -->
<!--   #        protein_original = protein_name_short) -->
<!--   select(all_of(c("id", # DSFbase id -->

<!--                   # assignments -->
<!--                   "subset", # subset of  -->
<!--                   "subsubset", # not yet different from subset -->
<!--                   "subsubset_f", # not yet different from subset -->

<!--                   ### data -->
<!--                   "Temperature",  -->
<!--                   "value",  -->
<!--                   "value_norm",  -->

<!--                   ### experimental annotations -->
<!--                   "protein_name_short", # protein name abbreviation -->
<!--                   "protein_name_long", # full, unabmiguous protein name -->
<!--                   "well",  -->
<!--                   "variable", # unique identifier pre-ID -->
<!--                   "exp_num",  -->
<!--                   "exp_summary",  -->
<!--                   "protein_concentration_uM", -->
<!--                   "dye",  -->
<!--                   "dye_concentration_uM", -->
<!--                   "buffer", -->
<!--                   "additive", -->
<!--                   "additive_description", -->
<!--                   "additive_concentration_uM", -->
<!--                   "thermocycling_protocol", -->
<!--                   "fluorescent_channel", -->
<!--                   "instrument", -->
<!--                   "additional_notes" -->
<!--                     ))) -->

<!-- annotated %>% nrow() # [1] 436730 -->
<!-- annotated_renamed %>% nrow() # [1] 436730 -->

<!-- annotated$variable %>% n_distinct() # [1] 6239 -->

<!-- # annotated_renamed %>% write_rds("../01_annotated_entries/protein_names/") -->

<!-- annotated_renamed %>% head() -->
<!-- ``` -->

# overwrite the protein names
```{r}

```


```{r}
dsfbase_annotated_original$subsubset %>% table()
```


Directories to save the outputs
```{r}
save_preliminary_to <- "/Users/taiaseanwu/Desktop/programming/dsfbase/20231205_version/02_combined_dsfbase/01_preliminary_subsets/data/"
save_preliminary_plots_to <- "/Users/taiaseanwu/Desktop/programming/dsfbase/20231205_version/02_combined_dsfbase/01_preliminary_subsets/plots/"

# create directories if they do not already exist
fs::dir_create(save_preliminary_to)
fs::dir_create(save_preliminary_plots_to)
```


```{r}
dsfbase_annotated_original <- read_rds("/Users/student/Desktop/2024-02-13 taia files/20231205_version/03_final_dsfbase/dsfbase_annotated.rds")
```


Add IDs
```{r}
dsfbase_preliminary <- add_IDs(annotated)
```

Save the preliminary version of DSFbase, for record keeping
```{r}
# data
write_rds(dsfbase_preliminary, glue::glue("{save_preliminary_to}dsfbase_annotated.rds"))

# plots
all_subsets <- c("errata", "SYPROcanon", "canon", "SYPROnoncanon", "noncanon")
lapply(all_subsets, plot_subset, dsfbase = dsfbase_preliminary, save_path = save_preliminary_plots_to, .test_subset = FALSE)
```

Save this tibble also into the assignment amendment folder to be read and used in the next notebook
```{r}
write_rds(dsfbase_preliminary, "/Users/taiaseanwu/Desktop/programming/dsfbase/20231205_version/02_combined_dsfbase/02_subset_amendments/to_reassign/dsfbase_to_update.rds")
```





