---
title: "Read, tidy, and add dye screen data to DSFbase"
output: html_notebook
---

In this notebook:
I. read in all dye screens, and assign curves to subsets in two steps
      - step 1: "hit"s in the best channel get "canon" (or "SYPROcanon", if the dye is SYPRO); 
                "sensitive" in the best channel get "noncanon" or "SYPROnoncanon"
      - step 2: manually update these subset assignments based on visual inspection of the plot
                - these manaul edits are captured in the add_all_dye_screens.R script

These subset assignments will likely be updated again after this. 

II. combine all dye screens into a single, tidy tibble,
      - each entry still has a unique variable, now containins experiment number, previous variable,  
  
III. add experimental annotations and save 

Next step: combine with non dye screen data and add IDs

```{r}
library(tidyverse)
library(fs)
library(testthat)
library(glue) # for print messages
source("R/functions/tests.R") # automated test for dsfbase experiments
source("R/functions/utils.R") 
source("R/functions/dye_screen_to_dsfbase.R") # functions to read and tidy dye screens for dsfbase
```


delete momentarily
```{r}
test_dye_screen <- tidy_1252("/Users/taiaseanwu/Desktop/programming/dsfbase/20231205_version/00_inputs/dye_screens/raw_dye_screens/Exp1252--20211206_all_dye_screens_collected/Exp1194_CHIP-full_screen_results.rds")

test_dye_screen$assignment |>  table()

 #Exp1194_CHIP
  dye_screen_to_dsfbase(dye_screen_dirs["Exp1194_CHIP"],
  save_path = .save_path, # min_range = .min_range,
   # save_data = .save_data,
   drop_from_canon = c("A18_Cy5_protein", "A23_TAMRA_protein"),
   add_to_noncanon = c("A18_Cy5_protein", "A23_TAMRA_protein"),
   drop_from_noncanon = c("A17_FAM_protein","A24_TAMRA_protein","C14_TAMRA_protein", "E11_Cy5_protein", "E17_Cy5_protein", "E20_Cy5_protein", "E8_FAM_protein", "G15_JOE_protein"), 
   ...)
```


----------  Run once: prepare files for reading and annotating
(i) Read in and tidy the conditions already created for all of the dye screens
```{r}
### Run once
# dye_screen_conditions <- read_rds("/Users/taiaseanwu/Box Sync/data/Exp1351--20220725_dye_screen_explorer_functions/3_read_by_app/conditions.rds")
# 
# # from Exp1352: Exp1351--20220725_dye_screen_explorer_functions/3_read_by_app/conditions.rds
# # write_rds(dye_screen_conditions, "/Users/taiaseanwu/Desktop/programming/dsfbase/20231205_version/00_inputs/dye_screens/dye_screen_annotations/dye_screen_experiment_summaries.rds")
# screen_summaries <- dye_screen_conditions |> 
#   mutate(exp_summary = glue("paDSF primary dye screen of {.data$total_dyes} Aurora library dyes with protein: '{.data$full_protein_name}'.")) |> 
#   relocate(exp_summary) |> 
#   replace_na(list(Notes = "none",
#                   protein_source = "unspecified",
#                   pdb_code = "none",
#                   uniprot_id = "none"
#                   ))  |> 
#   
#   # use this to join with the dye screens
#   unite(exp_protein, c(exp_num, protein_name), remove = FALSE) |> 
#   rename(buffer = screening_buffer,
#          protein_readable = full_protein_name,
#          protein_concentration_uM = screening_conc,
#          ) |>
#   mutate(additional_notes = paste0("Construct notes: ", Notes,
#                                "; Protein source: ", protein_source,
#                                "; PDB code: ", pdb_code,
#                                "; UNIPROT ID: ", uniprot_id
#                                )) |>
#   select(exp_protein, exp_num, exp_summary, protein_readable, protein_concentration_uM, buffer, additional_notes) |>
#   mutate(buffer = if_else(buffer == "WHAT IS NURRR1 BUFFER",
#                           true = "unspecified buffer",
#                           false = buffer))
# 
# write_rds(screen_summaries, "../00_inputs/dye_screens/dye_screen_annotations/dye_screen_experiment_summaries.rds")
```

(ii) Make directories to read in  data from Exp1252.
- The most complete and tidiest version of this data. 
- Includes automated channel selections for both hits and sensitive.
```{r}
### name the directories by protein name so they can be called in a human-readable way
non_caspase_screen_dir <- "../00_inputs/dye_screens/raw_dye_screens/Exp1252--20211206_all_dye_screens_collected/"
caspase_screen_dir <- "../00_inputs/dye_screens/raw_dye_screens/Exp1444--20230725_process_Tmas_for_caspase_screens_tidied_with_selections/"

dye_screens_no_caspases <- sort(fs::dir_ls(non_caspase_screen_dir))

screen_names <- dye_screens_no_caspases |> 
  gsub(non_caspase_screen_dir, "", x = _) |>  # drop the directory
  gsub("-full_screen_results.rds", "", x = _) # and the file extension

names(dye_screens_no_caspases) <- screen_names
  
## caspase screens (output file formatted slightly differently)
caspase_dye_screens <- fs::dir_ls(caspase_screen_dir)

caspase_screen_names <- caspase_dye_screens |> 
  gsub(caspase_screen_dir, "", x = _) |>  # drop the directory
  gsub("_df_alltidied_with_fit_selections.rds", "", x = _) # and the file extension

names(caspase_dye_screens) <- caspase_screen_names

#### combine and save
all_dye_screen_dirs <- c(dye_screens_no_caspases, caspase_dye_screens)

write_rds(all_dye_screen_dirs, "../00_inputs/dye_screens/raw_dye_screens/dye_screen_directories.rds")
```

---------- Read in all of the dye screens, implement manual subset assignment updates
```{r}
# contains a function which reads and adds all dye screens to dsfbase
source("R/scripts/add_all_dye_screens.R")

.save_individual_screens <- "../01_annotated_entries/dye_screens/individual_dye_screens/"

add_all_dye_screens(dye_screen_dirs = all_dye_screen_dirs,
                       .save_path = .save_individual_screens)
```

---------- Tidy and annotate dye screens
(i) Combine all dye screens into a single tibble
```{r}
ALL_DYE_SCREENS <- fs::dir_ls(.save_individual_screens, regexp = ".rds")

all_dye_screens_raw <- 
  lapply(ALL_DYE_SCREENS, read_rds) |> 
  bind_rows() |> 
  unite(variable, c(exp_num, variable, protein), sep = "__", remove = FALSE) |> 
  unite(exp_protein, c(exp_num, protein), remove = FALSE) # to join with sceen summary
```


(ii) Add entries from the original version of DSFbase which got missed by the new code
```{r}
##### ---- read in an tidy original dsfbase
dsfbase <- read_rds( "/Users/taiaseanwu/Desktop/programming/dsfbase/03_combined_data/dsfbase.rds") |>

  # add an exp_num column, to join with the annotations
  mutate(exp_num = gsub(pattern = "../02_aggregated_data/SYPRO_canon/|../02_aggregated_data/SYPRO_noncanon/|../02_aggregated_data/canon/|../02_aggregated_data/noncanon/|../02_aggregated_data/errata/|../02_aggregated_data/gotcha/|.rds",
                        replacement = "",
                        directory)) |>
  separate(exp_num, into = c("exp_num", "exp_name"), sep = "_", extra = "merge") |>
  select(-exp_name) |>

  # keep only the  dye screens
  filter(exp_num %in% all_dye_screens_raw$exp_num) |> 
  unite(variable, c(exp_num, variable, protein_original), sep = "__", remove = FALSE)

## compare to the new dsfbase dye screens
# same number of screens
dsfbase$exp_num |> n_distinct() # [1] 58
all_dye_screens_raw$exp_num |> n_distinct() # [1] 58

# different number of entries
dsfbase$variable |> n_distinct() # [1] [1] 893
all_dye_screens_raw$variable |>  n_distinct() # [1] 683

# dsfbase has five entries with duplicate variable names
# likely resulting from double-assignment -- not worth
# chasing down for five entries, so just drop these ones
dsfbase$id |> n_distinct() # [1] 898
double_assigned <- dsfbase |> select(variable, id) |> distinct() |> group_by(variable) |> tally() |> filter(n>1) |> pull(variable)

# take from original
vars_in_dsfbase <- unique(dsfbase$variable[!dsfbase$variable %in% annotated_dye_screen$variable])

### ---- check out just the dsfbase entries which are missing from the new dataset
dsfbase_missing <- dsfbase |> 
  filter(variable %in% vars_in_dsfbase)

# plot the missing entries and determine which are worth adding
plot_by_subset(dsfbase_missing, save_path = "/Users/taiaseanwu/Desktop/programming/dsfbase/20231205_version/00_inputs/dye_screens/",
               dataset_name = "dsfbase_missing_from_new_version")


## having examined the plot, all but a couple of p300 entries are worth adding
drop_from_missing <-  c("Ds0007__H15_FAM_protein__p300_KIX", "Ds0007__H3_JOE_protein__p300_KIX", "Ds0007__I3_JOE_protein__p300_KIX")


## ----- isolate just the entries to add
add_from_previous <- dsfbase |> 
   filter(variable %in% vars_in_dsfbase) |> 
   filter(!variable %in% drop_from_missing,
          !variable %in% double_assigned) |> 
  
  # change types to pass dataset test
  mutate(id = as.character(id),
         subset = as.character(subset)) |> 
  
  mutate(protein = protein_original) |> 
  select(-protein_original) |> 
  
  unite(exp_protein, c(exp_num, protein), remove = FALSE) 
# |> 
#   
#   left_join(screen_summaries, by = join_by(exp_num)) #, join = join_by(exp_num))

add_from_previous
```


```{r}
fix_protein_names

### filter the missing exp_proteins by exp_num ,and figure out what the protein name mismatches are
# write a case_when() to fix them

test_dataset(add_from_previous)
add_from_previous

annotated_dye_screen_raw

annotated_dye_screen_raw
all_dye_screens_raw

previous_exp_prot <- unique(add_from_previous$exp_protein))
sort(unique(add_from_previous$exp_protein))[!sort(unique(add_from_previous$exp_protein)) %in% sort(unique(screen_summaries$exp_protein))]

sort(unique(screen_summaries$exp_protein))

sort(unique(add_from_previous$exp_protein))





protein_rename

# [1] "Exp0620_NPAS2_PAS-A"            "Exp0621_PER2_PAS-AB_wt"         "Exp0673_GS_324S"                "Exp0674_GS_324C"                "Exp0732_Widom_601_DNA"         
#  [6] "Exp1246_SP214_caspase7_active"  "Exp1256_SP215_caspase1_zymogen" "Exp1257_SP216_caspase3_active"  "Exp1258_SP217_caspase6_active"  "Exp1259_SP218_caspase9_active" 
# [11] "Ds0031_GB1"
```


(iii) Join with experimental condition summaries 
```{r}
screen_summaries <- read_rds("../00_inputs/dye_screens/dye_screen_annotations/dye_screen_experiment_summaries.rds") |> 
  add_row("exp_protein" = "Exp0732_Widom_601_DNA", 
          "exp_num" = "Exp0732", 
          "exp_summary" = "paDSF primary dye screen of Aurora library dyes with protein: 'Widom 601 (DNA)'.", 
          "protein_readable" = "Widom 601 (DNA)", 
          "protein_concentration_uM" = 1, 
          "buffer" = "TAE", 
          "additional_notes" = "Construct notes: The Widom 601 DNA sequence, used to assemble nucleosomes in vitro; Protein source: Hayden Saunders, Narlikar Lab, UCSF",
          )

screen_summaries %>% select(exp_protein, protein_readable)


screen_summaries
```


```{r}
all_dye_screens_raw
 
annotated_dye_screen_raw <- 
  all_dye_screens_raw |> 
  mutate(protein = case_when(protein == "Widom_601_DNA" ~ "Widom 601 DNA")) |> 
  bind_rows(add_from_previous) |> 
  # fix the protein names which differ between raw data and annotations
  left_join(fix_protein_names, by = join_by(exp_num, exp_protein)) |> 
  mutate(exp_protein = case_when(exp_protein == matched_name ~ exp_protein,
                                 exp_protein != matched_name ~ matched_name,
                                 .default = exp_protein)) |> 
  

  left_join(screen_summaries, 
            by = join_by("exp_num","exp_protein")) |> 

  rename(dye_concentration_uM = dye_conc_uM,
         fluorescent_channel = channel_f,
         protein = protein_readable, 
         protein_original = protein) |> 
  
  # add the columns which all dye screens share
  mutate(additive = NA,
         additive_description = NA,
         additive_concentration_uM = NA,
         thermocycling_protocol = "continuous_1C_per_min_25_to_94",
          instrument = "qTower384G",
          directory = NA,
         id = "placeholder")
  
### ----  keep only the columns used in dsfbase
keep_cols <- c("id", "protein", "variable", "protein_original", "subset", "Temperature", "value", "well", "directory", "value_norm", "exp_num", "exp_summary", "protein_concentration_uM", "dye", "dye_concentration_uM", "buffer", "additive", "additive_description", "additive_concentration_uM", "thermocycling_protocol", "fluorescent_channel", "instrument", "additional_notes")

annotated_dye_screen <- 
  annotated_dye_screen_raw |> 
  select(all_of(keep_cols))

test_annotated_dataset(annotated_dye_screen)

annotated_dye_screen$variable |> n_distinct() # [1] 898
annotated_dye_screen$exp_num |> n_distinct() # [1] 58
```

```{r}
summarise_conditions <- function(annotated){
  n_experiments <- n_distinct(annotated$exp_num)
  
  missing_summary <- annotated |> 
    filter(is.na(exp_summary)) |> 
    distinct() |> 
    select(exp_num, exp_summary) |> 
    distinct() |> 
    group_by(exp_num) |> 
    tally()
}

  missing_summary <- annotated_dye_screen |> 
    filter(is.na(exp_summary)) |> 
    select(exp_num, exp_summary) |> 
    distinct() |> 
    group_by(exp_num) |> 
    tally()
  
  missing_summary
  
  annotated_dye_screen |> filter(is.na(exp_summary))

function (layout, plate_notes = "none", ...) 
{
    n_wells <- n_distinct(layout$well)
    n_variables <- length(names(layout)[!names(layout) %in% c("well", 
        "row", "column", "condition")])
    variables <- names(layout)[!names(layout) %in% c("well", 
        "row", "column", "condition")]
    plate_heading <- glue_col(.literal = TRUE, "Experiment containing {green {n_wells} wells}, with {green {n_variables}} {yellow experimental variables}")
    plate_msgs <- lapply(variables, summarise_variable, layout = layout)
    all_notes <- tryCatch(glue_col(.literal = TRUE, "{glue_collapse(plate_notes, sep = '\n ')}"), 
        error = function(e) {
            "Notes could not be printed."
        })
    var_summary <- glue_col(.literal = TRUE, "{plate_heading} \n \n{magenta {bold Notes:}} \n{plate_notes} \n{glue_collapse(plate_msgs, sep = '\n \n')}")
    print(var_summary)
}
```

Plot all subsets and save the final tibble
```{r}
plot_by_subset(annotated_dye_screen, "../01_annotated_entries/dye_screens/", "all_dye_screens")
```

(iii) Save the final single tibble
```{r}
# 683 entries (is that actually enough? I feel like that's not all of them .... )
write_rds(annotated_dye_screen, "../01_annotated_entries/dye_screens/all_dye_screens_annotated.rds")
```


After the fact -- 
Tally how many unique protein names there are
```{r}
annotated_dye_screen <- read_rds("../01_annotated_entries/dye_screens/all_dye_screens_annotated.rds")



annotated_dye_screen


annotated_dye_screen %>% head()

annotated_dye_screen$protein %>% unique()
annotated_dye_screen$protein_original %>% unique()

n_distinct(annotated_dye_screen$protein ) # [1] 56
n_distinct(annotated_dye_screen$protein_original) # [1] 50

annotated_dye_screen %>% filter(!is.na(protein_original)) %>% pull(protein) %>% unique()
```




